### 2024-03-09 paper/paper.qmd
update

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: <https://github.com/yangzhoucoco/Political-support-in-the-United-States.git>."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(here)
```

# Introduction

You can and should cross-reference sections and sub-sections. We use @citeR and @rohan.

The remainder of this paper is structured as follows. @sec-data....

# Data {#sec-data}

Some of our data is of penguins (@fig-vote),
```{r}
#| label: fig-vote
#| fig-cap: The distribution of presidential preferences, by gender, and highest education
#| echo: false
#| warning: false
#| message: false

ces2020 <- read_csv(here("data/analysis_data/analysis_data.csv"))

ces2020 |>
  ggplot(aes(x = education, fill = voted_for)) +
  stat_count(position = "dodge") +
  facet_wrap(facets = vars(gender)) +
  theme_minimal() +
  labs(
    x = "Highest education",
    y = "Number of respondents",
    fill = "Voted for"
  ) +
  coord_flip() +
  scale_fill_brewer(palette = "Set1") +
  theme(legend.position = "bottom")
```

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

analysis_data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))

analysis_data |> 
  ggplot(aes(x = width, y = length)) +
  geom_point(alpha = 0.8) +
  theme_minimal() +
  labs(x = "Wing width (mm)",
       y = "Wing length (mm)")
```

Talk way more about it.

# Model

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up

Define $y_i$ is the political preference of the respondent and equal to 1 if Biden and 0 if Trump. Then $\mbox{gender}_i$ is the gender of the respondent and $\mbox{education}_i$ is the education of the respondent.  
We could estimate the parameters using `stan_glm()`. Note that the model is a generally accepted short-hand.  In practice rstanarm converts categorical variables into a series of indicator variables and there are multiple coefficients estimated. In the interest of run-time we will randomly sample 1,000 observations and fit the model on that, rather than the full dataset.

#linear regression example
\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

#logistic regression example
\begin{align} 
y_i|\pi_i &\sim \mbox{Bern}(\pi_i) \\
\mbox{logit}(\pi_i) & = \beta_0+\beta_1 \times\mbox{gender}_i +\beta_2 \times \mbox{education}_i\\

\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}
We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

# Results

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

first_model <-
  readRDS(file = here::here("models/first_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

plot(first_model, "trace")

plot(first_model, "rhat")
```

\newpage

# References

### 2024-03-09 paper/paper.qmd
update paper

@@
 
-Some of our data is of penguins (@fig-vote),
+For the actual data we can use the 2020 Cooperative Election Study (CES) (@main_data)
 ```{r}
@@
 
-```{r}
-#| label: fig-bills
-#| fig-cap: Bills of penguins
-#| echo: false
-
-ggplot(penguins, aes(x = island, fill = species)) +
-  geom_bar(alpha = 0.8) +
-  scale_fill_manual(values = c("darkorange","purple","cyan4"),
-                    guide = "none") +
-  theme_minimal() +
-  facet_wrap(~species, ncol = 1) +
-  coord_flip()
-```
-
 Talk more about it.
@@
 (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)
-
-```{r}
-#| label: fig-planes
-#| fig-cap: Relationship between wing length and width
-#| echo: false
-#| warning: false
-#| message: false
-
-analysis_data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))
-
-analysis_data |> 
-  ggplot(aes(x = width, y = length)) +
-  geom_point(alpha = 0.8) +
-  theme_minimal() +
-  labs(x = "Wing width (mm)",
-       y = "Wing length (mm)")
-```
 
@@
 \mbox{logit}(\pi_i) & = \beta_0+\beta_1 \times\mbox{gender}_i +\beta_2 \times \mbox{education}_i\\
+\beta_0 &\sim \mbox{Normal}(0, 2.5)\\
+\beta_1 &\sim \mbox{Normal}(0, 2.5)\\
+\beta_2 &\sim \mbox{Normal}(0. 2.5)
+\end{align}
 
-\alpha &\sim \mbox{Normal}(0, 2.5) \\
-\beta &\sim \mbox{Normal}(0, 2.5) \\
-\gamma &\sim \mbox{Normal}(0, 2.5) \\
-\sigma &\sim \mbox{Exponential}(1)
-\end{align}
-We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
+We run the model in R [@citeR] using the `rstanarm` package of @rstanarm, `here` package of @here and `model_summary` package of @model_summary, we use the default priors from `rstanarm`
 
@@
 first_model <-
-  readRDS(file = here::here("models/first_model.rds"))
+  readRDS(file = here::here("model/first_model.rds"))
 ```
@@
   list(
-    "First model" = first_model
+    "Support Biden" = political_preferences
   ),
@@
 
-## Diagnostics
-
-@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...
-
-@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...
-
-```{r}
-#| echo: false
-#| eval: true
-#| message: false
-#| warning: false
-#| label: fig-stanareyouokay
-#| fig-cap: "Checking the convergence of the MCMC algorithm"
-#| fig-subcap: ["Trace plot", "Rhat plot"]
-#| layout-ncol: 2
-
-plot(first_model, "trace")
-
-plot(first_model, "rhat")
-```
-
 \newpage

### 2024-03-09 scripts/00-simulate_data.R
update simulated data

@@ -1,6 +1,6 @@
 #### Preamble ####
 # Purpose: Simulates... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
+# Author: Yang Zhou & Yuean Wang [...UPDATE THIS...]
 # Date: 11 February 2023 [...UPDATE THIS...]
 # Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
 # License: MIT
@@ -15,27 +15,27 @@ library(dplyr)
 #### Simulate data ####
 set.seed(853)
 
-num_obs <- 1000
+num_obs <- 800
 
 us_political_preferences <- tibble(
-  education = sample(0:4, size = num_obs, replace = TRUE),
-  gender = sample(0:1, size = num_obs, replace = TRUE),
-  support_prob = ((education + gender) / 5),
+  race = sample(0:5, size = num_obs, replace = TRUE),
+  lgbtq = sample(0:1, size = num_obs, replace = TRUE),
+  support_prob = ((race + lgbtq) / 5),
 ) |>
   mutate(
     supports_biden = if_else(runif(n = num_obs) < support_prob, "yes", "no"),
-    education = case_when(
-      education == 0 ~ "< High school",
-      education == 1 ~ "High school",
-      education == 2 ~ "Some college",
-      education == 3 ~ "College",
-      education == 4 ~ "Post-grad"
+    race = case_when(
+      race == 0 ~ "White",
+      race == 1 ~ "Black",
+      race == 2 ~ "Hispanic",
+      race == 3 ~ "Asian",
+      race == 4 ~ "Other"
     ),
-    gender = if_else(gender == 0, "Male", "Female")
+    lgbtq = if_else(lgbtq == 0, "LGBTQ", "Non_LGBTQ")
   ) |>
-  select(-support_prob, supports_biden, gender, education)
+  select(-support_prob, supports_biden, race, lgbtq)
 
 
 
 
-write.csv(us_political_preferences, "data/simulated_data/simulated_data.csv")
+write.csv(us_political_preferences, "data/simulate_data/simulate_data.csv")

### 2024-03-09 scripts/01-download_data.R
upload download data

@@ -14,16 +14,16 @@ library(tidyverse)
 
 
 #### Download data ####
-ces2020 <-
+ces2022 <-
   get_dataframe_by_name(
-    filename = "CES20_Common_OUTPUT_vv.csv",
-    dataset = "10.7910/DVN/E9N6PH",
+    filename = "CCES22_Common_OUTPUT_vv_topost.csv",
+    dataset = "10.7910/DVN/PR4L8P",
     server = "dataverse.harvard.edu",
     .f = read_csv
   ) |>
-  select(votereg, CC20_410, gender, educ)
+  select(votereg, presvote20post, race, sexuality)
 
-write_csv(ces2020, "data/raw_data/raw_data.csv")
+write_csv(ces2022, "data/raw_data/raw_data.csv")
 
 
 

### 2024-03-09 scripts/00-simulate_data.R
update change

@@ -18,9 +18,9 @@ set.seed(853)
 num_obs <- 800
 
 us_political_preferences <- tibble(
-  race = sample(0:5, size = num_obs, replace = TRUE),
-  lgbtq = sample(0:1, size = num_obs, replace = TRUE),
-  support_prob = ((race + lgbtq) / 5),
+  race = sample(0:4, size = num_obs, replace = TRUE),
+  gender = sample(0:1, size = num_obs, replace = TRUE),
+  support_prob = ((race + gender) / 5),
 ) |>
   mutate(
     supports_biden = if_else(runif(n = num_obs) < support_prob, "yes", "no"),
@@ -31,9 +31,9 @@ us_political_preferences <- tibble(
       race == 3 ~ "Asian",
       race == 4 ~ "Other"
     ),
-    lgbtq = if_else(lgbtq == 0, "LGBTQ", "Non_LGBTQ")
+    gender = if_else(gender == 0, "Male", "Female")
   ) |>
-  select(-support_prob, supports_biden, race, lgbtq)
+  select(-support_prob, supports_biden, race, gender)
 
 
 

### 2024-03-09 scripts/01-download_data.R

@@ -21,9 +21,9 @@ ces2022 <-
     server = "dataverse.harvard.edu",
     .f = read_csv
   ) |>
-  select(votereg, presvote20post, race, sexuality)
+  select(votereg, presvote20post, race, gender4)
 
-write_csv(ces2022, "data/raw_data/raw_data.csv")
+write_csv(ces2022, "data/raw_datas/raw_datas.csv")
 
 
 

### 2024-03-09 scripts/02-data_cleaning.R

@@ -11,37 +11,41 @@
 library(tidyverse)
 
 #### Clean data ####
-raw_data <- read_csv("data/raw_data/raw_data.csv")
+raw_data <- read_csv("data/raw_datas/raw_datas.csv")
 
 cleaned_data <-
   raw_data |>
   filter(votereg == 1,
-         CC20_410 %in% c(1, 2)) |>
+         presvote20post %in% c(1, 2)) |>
   mutate(
-    voted_for = if_else(CC20_410 == 1, "Biden", "Trump"),
+    voted_for = if_else(presvote20post == 1, "Biden", "Trump"),
     voted_for = as_factor(voted_for),
-    gender = if_else(gender == 1, "Male", "Female"),
-    education = case_when(
-      educ == 1 ~ "No HS",
-      educ == 2 ~ "High school graduate",
-      educ == 3 ~ "Some college",
-      educ == 4 ~ "2-year",
-      educ == 5 ~ "4-year",
-      educ == 6 ~ "Post-grad"
+    gender = if_else(gender4 == 0, "Male", "Female"),
+    race = case_when(
+      race == 1 ~ "White",
+      race == 2 ~ "Black",
+      race == 3 ~ "Hispanic",
+      race == 4 ~ "Asian",
+      race == 5 ~ "Native American",
+      race == 6 ~ "Middle Eastern",
+      race == 7 ~ "Two or more races",
+      race == 8 ~ "Other"
     ),
-    education = factor(
-      education,
+    race = factor(
+      race,
       levels = c(
-        "No HS",
-        "High school graduate",
-        "Some college",
-        "2-year",
-        "4-year",
-        "Post-grad"
+        "White",
+        "Black",
+        "Hispanic",
+        "Asian",
+        "Native American",
+        "Middle Eastern",
+        "Two or more races",
+        "Other"
       )
     )
   ) |>
-  select(voted_for, gender, education)
+  select(voted_for, gender4, race)
 
 
 #### Save data ####

### 2024-03-09 scripts/03-test_data.R
update change

@@ -13,10 +13,9 @@ library(tidyverse)
 library(testthat)
 
 #### Test data ####
-#12.3.1 test that
-simulated_data <- read.csv("data/simulated_data/simulated_data.csv")
+simulate_data <- read.csv("data/simulate_data/simulate_data.csv")
 test_that("Check class", {
-  expect_type(simulated_data$education, "character")
-  expect_type(simulated_data$gender, "character")
+  expect_type(cleaned_data$race, "character")
+  expect_type(cleaned_data$gender, "character")
 })
 

### 2024-03-09 scripts/04-model.R

@@ -11,14 +11,21 @@
 #### Workspace setup ####
 library(tidyverse)
 library(rstanarm)
+library(modelsummary)
 
 #### Read data ####
 analysis_data <- read_csv("data/analysis_data/analysis_data.csv")
 
 ### Model data ####
-political_preferences <-
+set.seed(853)
+
+ces2022_reduced <- 
+  ces2022 |> 
+  slice_sample(n = 500)
+
+us_political_preferences <-
   stan_glm(
-    factor(voted_for) ~ gender + education,
+    factor(voted_for) ~ gender4 + race,
     data = analysis_data,
     family = binomial(link = "logit"),
     prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
@@ -31,8 +38,16 @@ political_preferences <-
 
 #### Save model ####
 saveRDS(
-  political_preferences,
+  us_political_preferences,
   file = "model/first_model.rds"
+)
+
+
+modelsummary(
+  list(
+    "Support Biden" = us_political_preferences
+  ),
+  statistic = "mad"
 )
 
 

### 2024-03-09 scripts/00-simulate_data.R
update change

@@ -19,7 +19,7 @@ num_obs <- 800
 
 us_political_preferences <- tibble(
   race = sample(0:4, size = num_obs, replace = TRUE),
-  gender = sample(0:1, size = num_obs, replace = TRUE),
+  gender = sample(1:2, size = num_obs, replace = TRUE),
   support_prob = ((race + gender) / 5),
 ) |>
   mutate(
@@ -31,7 +31,7 @@ us_political_preferences <- tibble(
       race == 3 ~ "Asian",
       race == 4 ~ "Other"
     ),
-    gender = if_else(gender == 0, "Male", "Female")
+    gender = if_else(gender == 1, "Male", "Female")
   ) |>
   select(-support_prob, supports_biden, race, gender)
 

### 2024-03-09 scripts/02-data_cleaning.R

@@ -16,11 +16,12 @@ raw_data <- read_csv("data/raw_datas/raw_datas.csv")
 cleaned_data <-
   raw_data |>
   filter(votereg == 1,
-         presvote20post %in% c(1, 2)) |>
+         presvote20post %in% c(1, 2),
+         gender4 %in% c(1, 2)) |> 
   mutate(
     voted_for = if_else(presvote20post == 1, "Biden", "Trump"),
     voted_for = as_factor(voted_for),
-    gender = if_else(gender4 == 0, "Male", "Female"),
+    gender = if_else(gender4 == 1, "Male", "Female"),
     race = case_when(
       race == 1 ~ "White",
       race == 2 ~ "Black",

### 2024-03-10 paper/paper.qmd
update simulated data
update change

@@
 # Introduction
-
-You can and should cross-reference sections and sub-sections. We use @citeR and @rohan.
-
-The remainder of this paper is structured as follows. @sec-data....
+Cooperative Election Study (CES) (@main_data) aims to study American electoral dynamics during 2022 elections period
 
 # Data {#sec-data}
+For the actual data we can use the 2022 Cooperative Election Study (CES) (@main_data)
 
-For the actual data we can use the 2020 Cooperative Election Study (CES) (@main_data)
+## Source and Methodology
+
+## Variables
 ```{r}
-#| label: fig-vote
-#| fig-cap: The distribution of presidential preferences, by gender, and highest education
+#| label: fig-variables
+#| fig-cap: Brief summary of variables types
 #| echo: false
@@
 
-ces2020 <- read_csv(here("data/analysis_data/analysis_data.csv"))
+ces2022 <-  read_csv(file = here::here("data/raw_datas/raw_datas.csv"))
+    col_types =
+      cols(
+        "votereg" = col_integer(),
+        "presvote20post" = col_integer(),
+        "gender" = col_integer(),
+        "race" = col_integer()
+      )
+ces2022
+```
+  After downloading @dataverse, We using @get_dataframe_by_name to access the CES.
+We select and save the data that we are most care about, which are "votereg", "presvote20post", "race", and "gender4".
+"votereg" represent the voter registration status.
+To be more specific, whether they are registered to vote or not.
+"presvote20post" records the president that voter select in the election of 2020.
+“race" describe the voter's raical or ethnic group, and "gender4" refer to the gender of voters.
+  However, when we access the raw data, there are some variables that we are not interested in.
+Therefore, we use the codebook to delve into the details.
+We only care about the voter who are registered to vote, and we are mainly focus on investigating the voter who select Biden or Trump in 2020.
+We found out that when the "presvote20post" is 1, then this indicates the register vote for Biden, and when it is 2 represents that the voter stand for Trump.
+We use @tidyverse to filter to the voters that we care about and label them with meaningful title.
+In addition，CES also provide the information for the gender of the voter.
+However, we noticed that there are four types of gender, which are man, woman, non-binary, other, and none and we are more interested in the group of man and woman.
+Therefore, we filter the gender by using @tidyverse.
+When the variable "gender" is 1, this indicates "man", but we rename all "man" to "male".
+When the variable "gender" is 2, it refers to "woman".
+We also rename all "woman" to "female".
+Finally, the codebook also define different "race" from 1 to 8, which are White, Black, Hispanic, Asian, Native American, Middle Eastern, Two or more races, and other.
+We keep all those races because we are not only interested in the major racial group, but also curious about the respond from minority group.
+  To better understand the raw data, a summary table had been drawn in order to provide more details for each variables, explaining the variables we select.
 
-ces2020 |>
-  ggplot(aes(x = education, fill = voted_for)) +
+## Measurements
+```{r}
+#| label: fig-vote
+#| fig-cap: The distribution of presidential preferences, by gender, and race
+#| echo: false
+#| warning: false
+#| message: false
+
+ces2022 <- read_csv(here("data/analysis_data/analysis_data.csv"))
+
+ces2022 |>
+  ggplot(aes(x = race, fill = voted_for)) +
   stat_count(position = "dodge") +
-  facet_wrap(facets = vars(gender)) +
+  geom_text(stat='count', aes(label=..count..), position=position_dodge(width=0.9), vjust=-0.25, color="black") +
+  facet_wrap(facets = vars(gender4)) +
   theme_minimal() +
   labs(
-    x = "Highest education",
+    x = "Race",
     y = "Number of respondents",
@@
 
-And also planes (@fig-planes).
+And also planes (@fig-vote).
 (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)
@@
 Define $y_i$ is the political preference of the respondent and equal to 1 if Biden and 0 if Trump.
-Then $\mbox{gender}_i$ is the gender of the respondent and $\mbox{education}_i$ is the education of the respondent.
+Then $\mbox{gender}_i$ is the gender of the respondent and $\mbox{race}_i$ is the race of the respondent.
 We could estimate the parameters using `stan_glm()`.
@@
 In practice rstanarm converts categorical variables into a series of indicator variables and there are multiple coefficients estimated.
-In the interest of run-time we will randomly sample 1,000 observations and fit the model on that, rather than the full dataset.
+In the interest of run-time we will randomly sample 500 observations and fit the model on that, rather than the full dataset.
 
-#linear regression example
-\begin{align} 
-y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
-\mu_i &= \alpha + \beta_i + \gamma_i\\
-\alpha &\sim \mbox{Normal}(0, 2.5) \\
-\beta &\sim \mbox{Normal}(0, 2.5) \\
-\gamma &\sim \mbox{Normal}(0, 2.5) \\
-\sigma &\sim \mbox{Exponential}(1)
-\end{align}
-
-#logistic regression example
 \begin{align} 
@@
 
-first_model <-
+us_political_preferences <-
   readRDS(file = here::here("model/first_model.rds"))
@@
 
-modelsummary::modelsummary(
+modelsummary(
   list(
-    "Support Biden" = political_preferences
+    "Support Biden" = us_political_preferences
   ),
-  statistic = "mad",
-  fmt = 2
+  statistic = "mad"
 )
+
 ```
@@
 
-Weaknesses and next steps should also be included.
-
-\newpage
-
-\appendix
-
-# Appendix {-}
-
-# Additional data details
-
-# Model details {#sec-model-details}
-
-## Posterior predictive check
-
-In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...
-
-In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...
-
-```{r}
-#| eval: true
-#| echo: false
-#| message: false
-#| warning: false
-#| label: fig-ppcheckandposteriorvsprior
-#| layout-ncol: 2
-#| fig-cap: "Examining how the model fits, and is affected by, the data"
-#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]
-
-pp_check(first_model) +
-  theme_classic() +
-  theme(legend.position = "bottom")
-
-posterior_vs_prior(first_model) +
-  theme_minimal() +
-  scale_color_brewer(palette = "Set1") +
-  theme(legend.position = "bottom") +
-  coord_flip()
-```
-
 \newpage

### 2024-03-10 paper/datasheet_template.qmd
fill the datasheet

---
title: "Datasheet for 'A dataset'"
author: 
  - Yang Zhou
  - Yuean Wang
thanks: "Code and data are available at: LINK."
date: "`r Sys.time()`"
date-format: "09 March 2024"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

Extract of the questions from @gebru2021datasheets.

**Motivation**

1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.*
    - The Cooperative Election Study (CES) aims to study how Americans perceive and hold their representatives accountable during elections. Besides, the study also interested in understanding their voting behavior and how their behavior be affected by political geography and social context. They study the group by capturing mass data across most of legislative constituencies. CES aims to fill the gap of understanding the American electoral process by analyzing congressional elections and national surveys.

2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
    - The Cooperative Election Study. It form 62 research teams and organizations. 
3. *Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.*
    - CES is supported by the National Science Foundation (NSF). Award #2148907 is the associated grant it has. The grantors involve numerous teams and collaborations.
4. *Any other comments?*
    - Based on real data, the guide provide a deep research of understanding American electoral behavior and different impacts of social contexts on voting aspect. It might provide implication for analyzing the trend of American elections.

**Composition**

1. *What do the instances that comprise the dataset represent (for example, documents, photos, people, countries)? Are there multiple types of instances (for example, movies, users, and ratings; people and interactions between them; nodes and edges)? Please provide a description.*
	- The instances in CES 2022 dataset represent individual respondents attend in the survey, which designed to record various information related to electoral behaviour, political perspective and demographic characteristics. The The types of instances include election experience, contextual data, and demographic information.

2. *How many instances are there in total (of each type, if appropriate)?*
	- CES involves 60,000 cases. Those cases are based on the survey of adult pariticipants in 2022 fall.
3. *Does the dataset contain all possible instances or is it a sample (not necessarily random) of instances from a larger set? If the dataset is a sample, then what is the larger set? Is the sample representative of the larger set (for example, geographic coverage)? If so, please describe how this representativeness was validated/verified. If it is not representative of the larger set, please describe why not (for example, to cover a more diverse range of instances, because instances were withheld or unavailable).*
	- This dataset does not contain all possible instances. By contrast, it is more focus on drawn the sample from  a larger set of U.S. adult citizens.  
	  The sampling method used by YouGov in the CES involved a matched random sampling method. This method begins with a count of the target population, which for general population studies includes all adults and is usually counted through a comprehensive survey such as the American Community Survey. CES then draws a random sample from that target population, called the target sample.
	  The representativeness was validated by weighting procedures. This procedures aims to address any remaining imbalances among the matched sample. The sample is weighted to match the distribution of the frame across multiple demographic and political dimensions. The weighting process consists of two stages: entropy balancing, followed by iterative proportional fitting (tilting) of several key variables and their interactions.
4. *What data does each instance consist of? "Raw" data (for example, unprocessed text or images) or features? In either case, please provide a description.*
	- It consists demographic information, political opinions and behaviors, electoral experiences, voter validation an device and participation information. In terms of political opinions, it includes respondents' political affiliations, voting president and their positions on various policy issues and political figures.
5. *Is there a label or target associated with each instance? If so, please provide a description.*
	- No.
6. *Is any information missing from individual instances? If so, please provide a description, explaining why this information is missing (for example, because it was unavailable). This does not include intentionally removed information, but might include, for example, redacted text.*
	- Vote file miss matching might be one of missing information from individual instances. The CES relies on matching respondent to outside voter files. There might be some chance that name, address, or other details are mismatch with respondent, leading to mismatch between voting status and respondent.
7. *Are relationships between individual instances made explicit (for example, users' movie ratings, social network links)? If so, please describe how these relationships are made explicit.*
	- CES 2022 dataset does not buil up a explicitly model relationship between individual instances. Each instance in the CES dataset represents a single respondent's survey answers, capturing their demographic details, political views, voting behavior, and other relevant information.
8. *Are there recommended data splits (for example, training, development/validation, testing)? If so, please provide a description of these splits, explaining the rationale behind them.*
	- No.
9. *Are there any errors, sources of noise, or redundancies in the dataset? If so, please provide a description.*
	- Random measurement error might be one of potential errors. For example, some respondents provides wrong answer, which might lead to a number of respondents being incorrectly categorized.
10. *Is the dataset self-contained, or does it link to or otherwise rely on external resources (for example, websites, tweets, other datasets)? If it links to or relies on external resources, a) are there guarantees that they will exist, and remain constant, over time; b) are there official archival versions of the complete dataset (that is, including the external resources as they existed at the time the dataset was created); c) are there any restrictions (for example, licenses, fees) associated with any of the external resources that might apply to a dataset consumer? Please provide descriptions of all external resources and any restrictions associated with them, as well as links or other access points, as appropriate.*
	- No, it does not link to external source. This dataset is mainly rely on survey collection of individual participants.Voter file matching might be an external consideration. Data for the CES 2022 study, including vote validation for all respondents, is archived and available at the Harvard University Dataverse. The restriction might be it does not include a specific restriction related to the TargetSmart database or other external resources used for voter file matching and verification are not detailed.
11. *Does the dataset contain data that might be considered confidential (for example, data that is protected by legal privilege or by doctor-patient confidentiality, data that includes the content of individuals' non-public communications)? If so, please provide a description.*
	- he CES 2022 dataset consists primarily of structured survey data collected from respondents about their political views, behaviors, and demographic information. Such data is generally not subject to legal privileges such as doctor-patient confidentiality or confidentiality of legal communications.
12. *Does the dataset contain data that, if viewed directly, might be offensive, insulting, threatening, or might otherwise cause anxiety? If so, please describe why.*
	- In terms of Racial and Sexual Agreement, it might be offensive for the respondent, especially when the question design in a way that might present bias.
13. *Does the dataset identify any sub-populations (for example, by age, gender)? If so, please describe how these subpopulations are identified and provide a description of their respective distributions within the dataset.*
	- There are lots of sub-population in the dataset. 
	1)Gender: The dataset categorizes respondents into "Man", "Woman", "Non-binary", and "Other", allowing for gender-based analyses.
	2)Race: The dataset categorizes respondents into "White", "Black", "Hispanic", "Asian", "Native American", "Middle Eastern", "Two or more races", and "Other"
	3)Education: Respondents' highest education levels are detailed, ranging from no high school diploma ("No HS") to postgraduate degrees
	4)Political Affiliation: The dataset records respondents' party affiliation, including "Democrat", "Republican", and "Independent/Other".
	5)Age: The dataset provide age range  (e.g., 18-29, 30-44, 45-64, 65 and over).

14. *Is it possible to identify individuals (that is, one or more natural persons), either directly or indirectly (that is, in combination with other data) from the dataset? If so, please describe how.*
	- No, all the dataset is anomymize.
15. *Does the dataset contain data that might be considered sensitive in any way (for example, data that reveals race or ethnic origins, sexual orientations, religious beliefs, political opinions or union memberships, or locations; financial or health data; biometric or genetic data; forms of government identification, such as social security numbers; criminal history)? If so, please provide a description.*
	- Yes, it includes race, sexual orientation, religious, political opinion, transgender status, health data and so on. For example, respondents are asked to answer their sexual orientation, with options including heterosexual/straight, lesbian/gay, bisexual, and others.
16. *Any other comments?*
	- No

**Collection process**

1. *How was the data associated with each instance acquired? Was the data directly observable (for example, raw text, movie ratings), reported by subjects (for example, survey responses), or indirectly inferred/derived from other data (for example, part-of-speech tags, model-based guesses for age or language)? If the data was reported by subjects or indirectly inferred/derived from other data, was the data validated/verified? If so, please describe how.*
	- The data associated with each instance in the CES 2022 was primarily acquired through survey responses reported directly by the subjects. The survey was conducted online by YouGov and involved a methodology known as sample matching.The target population is first counted and then a representative sample is selected from a non-randomly selected group of respondents.
  - Regarding the data segments concerning voter validation, the process involved aligning individual entries with the TargetSmart database, which contains records of U.S. registered voters. This alignment aimed to confirm the accuracy of survey respondents' claims about their voter registration and their actual voting activity in both the primary and general elections of 2022.
2. *What mechanisms or procedures were used to collect the data (for example, hardware apparatuses or sensors, manual human curation, software programs, software APIs)? How were these mechanisms or procedures validated?*
	- The CES 2022 data was collected through an online survey conducted by YouGov. They employed  "sample matching" methodology, which fit with online access panels.This method identify available respondents who are very similar in terms of measured characteristics to each member of the target sample. The total distance is calculated as the weighted sum of these individual distances on all attributes, and the weights can be adjusted for variables that are important to the study. This approach allows matched samples to closely represent the characteristics of the target population.
3. *If the dataset is a sample from a larger set, what was the sampling strategy (for example, deterministic, probabilistic with specific sampling probabilities)?*
	- The CES 2022 dataset's sampling strategy employed YouGov’s matched random sample methodology. 
4. *Who was involved in the data collection process (for example, students, crowdworkers, contractors) and how were they compensated (for example, how much were crowdworkers paid)?*
	- . The CES involved 60 parties and research teams. The dataset does not provide specific details on how individuals be compensated.
5. *Over what timeframe was the data collected? Does this timeframe match the creation timeframe of the data associated with the instances (for example, recent crawl of old news articles)? If not, please describe the timeframe in which the data associated with the instances was created.*
	- Collected over two time frame: the first period is the pre-election data collection occurred from September 29 to November 8, 2022,and the second period is  post-election data was gathered from November 10 to December 15, 2022.The timeframe is relevant to survey participants about their opinions, voting intention in 2022 election.
6. *Were any ethical review processes conducted (for example, by an institutional review board)? If so, please provide a description of these review processes, including the outcomes, as well as a link or other access point to any supporting documentation.*
	-  The dataset does not provide explicit details regarding any ethical review processes.
7. *Did you collect the data from the individuals in question directly, or obtain it via third parties or other sources (for example, websites)?*
	- The data for the 2022 Cooperative Election Study (CES) was collected directly from individuals through a survey conducted over the internet by YouGov.
8. *Were the individuals in question notified about the data collection? If so, please describe (or show with screenshots or other information) how notice was provided, and provide a link or other access point to, or otherwise reproduce, the exact language of the notification itself.*
	-Yes, because it is conducteddirectly from individuals through a survey conducted by YouGov over the internet. Cooperative Election Study (CES) or provide the exact language used in the notification. 
9. *Did the individuals in question consent to the collection and use of their data? If so, please describe (or show with screenshots or other information) how consent was requested and provided, and provide a link or other access point to, or otherwise reproduce, the exact language to which the individuals consented.*
	- The individuals participating in the 2022 Cooperative Election Study (CES) did provide their consent for data collection.The respondent will be asked if they agree to attend in the survey by inquired "Consent to participate: Do you agree to participate in the study?" The exact language used to request consent, is straightforward.
10. *If consent was obtained, were the consenting individuals provided with a mechanism to revoke their consent in the future or for certain uses? If so, please provide a description, as well as a link or other access point to the mechanism (if appropriate).*
	- The dataset does not provide specific information about whether individuals were given a mechanism to revoke their consent after agreeing to participate in the 2022 Cooperative Election Study (CES) or for certain uses of their data. 
11. *Has an analysis of the potential impact of the dataset and its use on data subjects (for example, a data protection impact analysis) been conducted? If so, please provide a description of this analysis, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- TBD
12. *Any other comments?*
	- TBD

**Preprocessing/cleaning/labeling**

1. *Was any preprocessing/cleaning/labeling of the data done (for example, discretization or bucketing, tokenization, part-of-speech tagging, SIFT feature extraction, removal of instances, processing of missing values)? If so, please provide a description. If not, you may skip the remaining questions in this section.*
	- TBD
2. *Was the "raw" data saved in addition to the preprocessed/cleaned/labeled data (for example, to support unanticipated future uses)? If so, please provide a link or other access point to the "raw" data.*
	- TBD
3. *Is the software that was used to preprocess/clean/label the data available? If so, please provide a link or other access point.*
	- TBD
4. *Any other comments?*
	- TBD

**Uses**

1. *Has the dataset been used for any tasks already? If so, please provide a description.*
	- TBD
2. *Is there a repository that links to any or all papers or systems that use the dataset? If so, please provide a link or other access point.*
	- TBD
3. *What (other) tasks could the dataset be used for?*
	- TBD
4. *Is there anything about the composition of the dataset or the way it was collected and preprocessed/cleaned/labeled that might impact future uses? For example, is there anything that a dataset consumer might need to know to avoid uses that could result in unfair treatment of individuals or groups (for example, stereotyping, quality of service issues) or other risks or harms (for example, legal risks, financial harms)? If so, please provide a description. Is there anything a dataset consumer could do to mitigate these risks or harms?*
	- TBD
5. *Are there tasks for which the dataset should not be used? If so, please provide a description.*
	- TBD
6. *Any other comments?*
	- TBD

**Distribution**

1. *Will the dataset be distributed to third parties outside of the entity (for example, company, institution, organization) on behalf of which the dataset was created? If so, please provide a description.*
	- TBD
2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
	- TBD
3. *When will the dataset be distributed?*
	- TBD
4. *Will the dataset be distributed under a copyright or other intellectual property (IP) license, and/or under applicable terms of use (ToU)? If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
	- TBD
5. *Have any third parties imposed IP-based or other restrictions on the data associated with the instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
	- TBD
6. *Do any export controls or other regulatory restrictions apply to the dataset or to individual instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
	- TBD
7. *Any other comments?*
	- TBD

**Maintenance**

1. *Who will be supporting/hosting/maintaining the dataset?*
	- The dataset for the CES 2022 is maintained and hosted by the Harvard University Dataverse.
2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
	- People can directly contact The Harvard University Dataverse platform.
3. *Is there an erratum? If so, please provide a link or other access point.*
	- No
4. *Will the dataset be updated (for example, to correct labeling errors, add new instances, delete instances)? If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
	- The guide does not provide detail information about update.
5. *If the dataset relates to people, are there applicable limits on the retention of the data associated with the instances (for example, were the individuals in question told that their data would be retained for a fixed period of time and then deleted)? If so, please describe these limits and explain how they will be enforced.*
	- The CES Guide 2022 does not provide specific information regarding limits on the retention of data associated with the instances.
6. *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
	- The guide does not discuss about the policies regarding the support, hosting, or maintenance of older versions of the dataset.
7. *If others want to extend/augment/build on/contribute to the dataset, is there a mechanism for them to do so? If so, please provide a description. Will these contributions be validated/verified? If so, please describe how. If not, why not? Is there a process for communicating/distributing these contributions to dataset consumers? If so, please provide a description.*
	- The guide does not include a explicit mechanism for others to extend to the dataset.
8. *Any other comments?*
	- No

\newpage

# References

### 2024-03-10 paper/datasheet_template.qmd
update change

@@
 If so, please provide a description of this analysis, including the outcomes, as well as a link or other access point to any supporting documentation.*
-	- TBD
+	- The provided CES Guide 2022 document does not specifically describe conducting a data protection impact analysis. It emphasizes on on the methodology, sample matching, data collection, 
 12. *Any other comments?*
-	- TBD
+	- No
 
@@
 If not, you may skip the remaining questions in this section.*
-	- TBD
+	- Yes, CES involves some data preprocessing, cleaning, and labeling to make sure the quality of the data.
+The descriptions have been included in the sampling methodology, matching procedures, and weighting processes.
+CES done 3 things, which are sampling and sample matching, weighting, and vote validation.To be more specific, in order to correct for any residual imbalances between the matched sample and the target population, the CES data was weight through 2 steps.
+First, using entropy balancing to match the distributions of the frame on key demographic variables (age, gender, education, race, etc.), and then using iterative proportional fitting ("raking") on additional variables (like voter registration status and 2020 Presidential vote choice) to further refine the representativeness of the sample.
 2.
@@
 If so, please provide a link or other access point to the "raw" data.*
-	- TBD
+	- The CES Guide 2022 does not explicitly mention whether the "raw" data save in addition to the preprocessed/cleaned/labeled data.
 3. *Is the software that was used to preprocess/clean/label the data available? If so, please provide a link or other access point.*
-	- TBD
+	- No.
 4. *Any other comments?*
-	- TBD
+	- No.
 
@@
 1. *Has the dataset been used for any tasks already? If so, please provide a description.*
-	- TBD
+	- The CES Guide 2022 does not provide specific examples of tasks for which the dataset has already been used.
 2. *Is there a repository that links to any or all papers or systems that use the dataset? If so, please provide a link or other access point.*
-	- TBD
+	- The CES Guide 2022 does not explicitly mention a repository that links to paper.
 3. *What (other) tasks could the dataset be used for?*
-	- TBD
+	- There are multiple task that the dataset can be used for. For example, to analyze voting behavior and study the impact of socioeconomic factor on political outcome.
 4.
@@
 Is there anything a dataset consumer could do to mitigate these risks or harms?*
-	- TBD
+	- Yes.The methodology section details efforts to create a representative sample and address potential biases through sample matching, weighting, and vote validation in order to avoid representation bias.The customer can ensure all research complies with applicable laws, ethical standards, and best practices for data privacy and protection.
 5. *Are there tasks for which the dataset should not be used? If so, please provide a description.*
-	- TBD
+	- No.
 6. *Any other comments?*
-	- TBD
+	- No.
 
@@
 If so, please provide a description.*
-	- TBD
+	- Yes, it will.
+It indicated that the data for the Cooperative Election Study (CES) 2022 is available at the Harvard University Dataverse.
+This can be seem as the dataset is accessible to third parties outside of the institutions directly involved in the creation of the dataset, such as Harvard University and YouGov.
 2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
-	- TBD
+	- The Cooperative Election Study (CES) 2022 will be distributed through the Harvard University Dataverse.
+This distribution method ensures that the dataset is accessible for academic and research purposes.
+The DOI for the Cooperative Election Study Common Content 2022 is https://doi.org/10.7910/DVN/PR4L8P,
 3. *When will the dataset be distributed?*
-	- TBD
+	- Dataset is distributed in two period: first, on March 20, 2023.
+It included the CES 2022 Common Content, which is the data collected that is common across all participating research teams.The second period is on September 8, 2023, it included vote validation for all respondents, enhancing the dataset's utility for electoral research by verifying the voting behavior reported by the survey participants.
 4.
@@
 If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
-	- TBD
+	- No.
 5.
@@
 If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
-	- TBD
+	- No.
 6.
@@
 7. *Any other comments?*
-	- TBD
+	- No.
 

### 2024-03-10 paper/datasheet_template.qmd
update change

@@
 thanks: "Code and data are available at: LINK."
-date: "`r Sys.time()`"
+date: "`09 March 2024`"
 date-format: "09 March 2024"
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: "The CES 2022 dataset, collected through an online survey by YouGov, encompasses 60,000 instances representing U.S.
+adult citizens' electoral behaviors, political opinions, and demographic characteristics.
+The instances are detailed and categorized by election experiences, contextual data, demographic information (e.g., gender, race, education), political affiliations, and opinions on various policy issues.
+The dataset employs a matched random sampling methodology, with its representativeness validated through a two-stage weighting process involving entropy balancing and iterative proportional fitting.
+Preprocessing included sample matching, weighting, and vote validation, ensuring data quality and representativenes in order to avoid representative bias."
 format: pdf
@@
 
-1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.*
+1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description
     - The Cooperative Election Study (CES) aims to study how Americans perceive and hold their representatives accountable during elections.
@@
 If so, please provide a description.*
-	- he CES 2022 dataset consists primarily of structured survey data collected from respondents about their political views, behaviors, and demographic information.
+	- The CES 2022 dataset consists primarily of structured survey data collected from respondents about their political views, behaviors, and demographic information.
 Such data is generally not subject to legal privileges such as doctor-patient confidentiality or confidentiality of legal communications.

### 2024-03-10 paper/datasheet_template.qmd
update change

@@
   - Yuean Wang
-thanks: "Code and data are available at: LINK."
+thanks: "Code and data are available at: <https://github.com/yangzhoucoco/Political-support-in-the-United-States.git.>"
 date: "`09 March 2024`"

### 2024-03-11 paper/paper.qmd
update change
Update paper.qmd

@@
 date-format: long
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: 
+There is no other nation in the world that conducts elections the way the United States does.
+Local government representatives oversee elections in around 8,000 distinct jurisdictions.
+They are then under the general supervision of authorities, who are frequently selected through election procedures or partisan appointees.
+Typically, the voter liaison at the polling place is a temporary worker who works unpaid for a single day and only gets a few hours of training.
+These distinctive characteristics of our electoral system, along with the fact that Americans vote more frequently than citizens in other countries on a wider range of issues and positions, create special difficulties for the efficient administration of elections that voters across demand and deserve.
+None of the other nations' electoral systems display all or any of these traits, but none have the same mix of US administrative traits.
+The quality of administration differs from jurisdiction to jurisdiction and even from polling place to polling place because of decentralization and dependence on volunteers.
+Because partisan officials will be involved, accusations of partisanship regarding the rules or their interpretation may arise based on the outcome of the judgments made by the officials and who stands to gain from it.
+The quantity and variety of democratic options in protracted elections have outpaced voters' attention spans and cognitive capacities.
+These distinguishing characteristics of our voting system contribute to the issues seen in the most recent elections.
+This paper is mainly based on the 2022 US election.
 format: pdf
@@
 # Introduction
-Cooperative Election Study (CES) (@main_data) aims to study American electoral dynamics during 2022 elections period
-
+The goal of the Cooperative Election Study (CES) is to investigate how Americans vote and perceive their electoral experiences, how they hold their representatives accountable in elections, and how their behavior and experiences vary depending on the political climate and social milieu.
+The study used an extremely large sample that allowed it to account for variations across different legislative districts.
+Actually, the sample size at the state level is sufficient to measure the voter preference distribution within the majority of states with a respectable degree of accuracy.
+60 teams participated in 2022CES, which resulted in a 60,000-case generic content sample. 
+Fall of 2022 saw the recruitment of study participants.
+Every research team invested in a 1,000-person nationwide sample survey from Redwood City, California-based YouGov.
+Two waves of interviewing were used for the 2022 survey.
+Pre-election surveys were filled out on the spot between September 29 and November 8.
+The post-election campaigning frenzy took place between November 10 and December 15.
+For every 1,000 respondents, half of the questions had common material while the other half were fully created and managed by each study team.
+Questions that are common to all team modules and have a sample size equal to the total sample size of all team modules make up common content.
+Every one of the sixty teams bought a 1,000-person survey.
+Every case was chosen online, and YouGov created a corresponding random sample for this investigation.
+The first data release happened on March 20, 2023.
+The Harvard University database contains archived and accessible data from this investigation.
+Vote verification is included in data release 2 for all respondents.
+The study on CES 2022 is still under progress.
+Using a large-scale national survey, the Collaborative Congressional Election project was founded in 2006 to investigate congressional elections and representation.
+The project built upon the analysis conducted by the Public Opinion Research and Training Lab at the Massachusetts Institute of Technology in 2005.
 # Data {#sec-data}
@@
 ## Source and Methodology
+
+## Sampling and Sampling Matching
+The CES 2022 dataset is a sample of adult U.S.
+citizens, taken from a considerably larger population, rather than an exhaustive list of all possible cases in the target population.
+The sample was deliberately created to be a true reflection of the population of the United States and to capture the variations among the different legislative districts for in-depth examination in the majority of states.
+Through the Internet, YouGov conducted the CES 2022 survey.
+60,000 adults were interviewed between September and November 2022 (pre-election data) and November and December 2022 (post-election data) for the Common Opinion.
+The YouGov matching approach for random sampling was used.
+YouGov employed the matched random sampling method at CES among other sampling techniques.
+The first step in this process is to count the target population, which in the case of general population research consists of all adults.
+This is typically done by using an extensive survey such as the American Community Survey.
+The target sample is then selected at random by CES from this target population.
+However, because it is frequently impractical to make direct contact with these individuals, a matching sample is chosen from among selectable respondents who share the same characteristics as the target sample.
+This selection process is carried out based on a multitude of attributes available in the voter and consumer databases.
+## Weightening
+A weighting process is used to account for any residual imbalances between the matched samples, therefore rigorously verifying the representativeness of CES samples.
+The weighting of the sample was adjusted to align with the framework's distribution along several demographic and political aspects.
+Entropy balancing and iterative proportional fitting (sequencing) of multiple important variables and their interactions comprise the first stage of the weighting process.
+The sample is also thought to be representative of every state for the survey's common content and takes into account changes for statewide political races.
+There are two steps involved in selecting samples when utilizing the matching approach.
+First, select a sample at random from the intended audience.
+This sample is known as the target sample.
+The process of choosing a "representative" sample from a non-random sample of responders is known as sample matching.
+Although it works well for Web access panels, it may also be applied to other survey kinds, such phone surveys.
+The target population is enumerated before sample matching begins.
+All adults are the target group for general population studies, and they can be counted using either a top-notch survey like the American Community Survey or the decennial Census.
+This is referred to as a sampling frame in other contexts, although unlike traditional sampling, the sample is not taken out of the frame.
+Using traditional sampling, participants in the study are chosen at random from a framework for sampling.
+Because not every person in the framework has access to contact information, particularly email addresses, and because declining to participate would raise the expense of sampling in this manner, it could not be practical or cost-effective.
+##Vote Vaildation
 

### 2024-03-11 paper/paper.qmd
Update paper.qmd

@@
 
-If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
+If my paper were 10 pages, then should be be at least 2.5 pages.
+The discussion is a chance to show off what you know and what you learnt from all this.
+Logistic regression is also known as generalized linear regression model, and its form is basically the same as that of linear regression model.
+The biggest difference lies in their different dependent variables.
+If it is continuous, it is multiple linear regression.
+If it is a binomial distribution, it is Logistic regression.
+Although Logistic regression has the name "regression", it is actually a classification method, mainly used for binary classification problems (that is, there are only two outputs, each representing two categories), but also can handle multiple classification problems.
+Linear regression is used to predict continuous variables, whose value range is (- ", + "), while logistic regression model is used to predict categories.
+For example, using logistic regression model to predict whether an item belongs to class A or Class B essentially predicts the probability that the item belongs to class A or class B, and the value range of probability is 0~1.
+Therefore, it is not possible to predict the probability directly with the linear regression equation, which involves the Sigmoid function, which converts the values of the range (-∞, +∞) to the range (0,1).
 
 ## Second discussion point
+In summary, the essence of logistic regression model is to transform the linear regression model Q through a nonlinear Sigmoid function to obtain a probability value between 0 and 1.
+For binary classification problem (classification 0 and 1), the probability of predicting the classification as 1(or the classification with a larger value in the binary classification) can be calculated using the formula shown below.
+df has a total of about 7000 groups of historical data, of which about 2000 groups are lost customers, about 5000 groups are not lost customers will "whether to lose" as the target variable, other fields as characteristic variables, through some basic information and transaction records of a customer to predict whether he will lose, or judge the probability of loss.
 
 ## Third discussion point
-
+The training set is used to train the data and build the model, and the test set is used to check the effect of the model built after training.
+The purpose of dividing the training set and the test set is to evaluate the model, and to optimize the model through the test set.
+Dividing the training set and the test set is also, in part, to check for overfitting of the model.
 ## Weaknesses and next steps

### 2024-03-11 paper/paper.qmd
Update paper.qmd

@@
 ## First discussion point {#sec-first-point}
-
-If my paper were 10 pages, then should be be at least 2.5 pages.
-The discussion is a chance to show off what you know and what you learnt from all this.
 Logistic regression is also known as generalized linear regression model, and its form is basically the same as that of linear regression model.
@@
 Dividing the training set and the test set is also, in part, to check for overfitting of the model.
+
 ## Weaknesses and next steps

### 2024-03-11 paper/paper.qmd
Update paper.qmd

@@
 # Data {#sec-data}
-For the actual data we can use the 2022 Cooperative Election Study (CES) (@main_data)
+The 2022 Cooperative Election Study (CES) (@main_data) involved significant data preprocessing, cleaning, and labeling efforts to ensure the quality and representativeness of the survey data.
+These efforts are elaborated on through descriptions of sampling methodology, matching procedures, and weighting processes as outlined in the CES Guide 2022.
 
@@
 ##Vote Vaildation
+The CES incorporated vote validation to verify the accuracy of respondents’ reported voting behaviors.
+Individual records were matched to the TargetSmart database of registered voters, and only records with a high level of confidence were considered matched.
+This process helped identify respondents who voted in the 2022 General and Primary Elections, as well as their modes of voting (e.g., absentee, early, mail, etc.).
+This validation step is crucial for analyses focused on voting behaviors and ensures that the CES data reflects actual voter participation.
+
+These methodologies indicate a comprehensive approach to data preprocessing, cleaning, and labeling within the CES 2022, aiming to enhance the accuracy, reliability, and representativeness of the survey data.
 

### 2024-03-11 paper/paper.qmd
Update paper.qmd

@@
 # Data {#sec-data}
+
+### Source and Methodology
 The 2022 Cooperative Election Study (CES) (@main_data) involved significant data preprocessing, cleaning, and labeling efforts to ensure the quality and representativeness of the survey data.
@@
 
-## Source and Methodology
-
-## Sampling and Sampling Matching
+### Sampling and Sampling Matching
 The CES 2022 dataset is a sample of adult U.S.
@@
 This selection process is carried out based on a multitude of attributes available in the voter and consumer databases.
-## Weightening
+
+### Weightening
 A weighting process is used to account for any residual imbalances between the matched samples, therefore rigorously verifying the representativeness of CES samples.
@@
 Because not every person in the framework has access to contact information, particularly email addresses, and because declining to participate would raise the expense of sampling in this manner, it could not be practical or cost-effective.
-##Vote Vaildation
+
+### Vote Vaildation
 The CES incorporated vote validation to verify the accuracy of respondents’ reported voting behaviors.

### 2024-03-11 paper/paper.qmd
Update paper.qmd

@@
 The project built upon the analysis conducted by the Public Opinion Research and Training Lab at the Massachusetts Institute of Technology in 2005.
+
 # Data {#sec-data}
 
-### Source and Methodology
+## Source and Methodology
 The 2022 Cooperative Election Study (CES) (@main_data) involved significant data preprocessing, cleaning, and labeling efforts to ensure the quality and representativeness of the survey data.

### 2024-03-12 paper/paper.qmd
Update paper.qmd

@@
 
-We expect a positive relationship between the size of the wings and time spent aloft. In particular...
+We expect a positive relationship between the size of the wings and time spent aloft. Logistic regression models learn and predict very quickly
+Fast, because logistic regression is a linear model, its decision function is a very simple linear function, so its computational complexity is low.
+Logistic regression model is easy to interpret, and the coefficient of the model can give the degree of influence of each feature on the model.
+This can be used in real business applications to help decision makers better understand the model's predictions.
+In addition, logistic regression models can handle large scale data well, because logistic regression models only need to dimension a small number of parameters to adapt well to a large number of parameters.
 
@@
 
-Our results are summarized in @tbl-modelresults.
+Our results are summarized in @tbl-modelresults.Logistic regression is a common classification algorithm used to predict binary classification problems.
+In logistic regression, the probability that a sample belongs to a certain class is determined by mapping the input data to a probability range between 0 and 1 using a logical function, such as the sigmoid function.
+When interpreting the results of logistic regression models.
+Logistic regression models can provide coefficients (or weights) for each feature variable that represent the relative importance of the feature.
+The positive and negative symbols of the coefficient can tell us whether the feature has positive or negative influence on the target category, and the absolute value of the coefficient can map the importance of the feature to the target category.
 
@@
 
-## First discussion point {#sec-first-point}
+## application of Logistic regression {#sec-first-point}
 Logistic regression is also known as generalized linear regression model, and its form is basically the same as that of linear regression model.
@@
 
-## Second discussion point
+## linear regression model
 In summary, the essence of logistic regression model is to transform the linear regression model Q through a nonlinear Sigmoid function to obtain a probability value between 0 and 1.
@@
 
-## Third discussion point
+## model building
 The training set is used to train the data and build the model, and the test set is used to check the effect of the model built after training.

### 2024-03-12 paper/paper.qmd
Update paper.qmd

@@
 
+Logistic regression can only deal with linearly separable problems, and for nonlinear separable data, logistic regression will be poor.
+Logistic regression is sensitive to outliers, and if there are outliers in the data, the effect of logistic regression may be affected.
+Finally, logistic regression can usually only handle binary classification problems, and for multi-classification problems, some additional processing is required.
+If the sample size is insufficient or the features are too complex, logistic regression is prone to overfitting.
+
 \newpage

### 2024-03-12 paper/paper.qmd
Update paper.qmd

@@
 author: 
-  - First author
+  - Dong Jun Yoon
   - Another author
@@
 ```
+The collected dataset from the Cooperative Election Study (CES) offers a comprehensive view of U.S.
+adult citizens' electoral behaviors, political opinions, and demographic characteristics.
+The CES 2022 dataset, gathered through an online survey by YouGov, encompasses 60,000 instances, meticulously detailed and categorized by various factors such as election experiences, contextual data, demographic information (e.g., gender, race, education), political affiliations, and opinions on various policy issues.
+This dataset ensures a reliable representation of the population through its meticulous sampling methodology and validation processes, guaranteeing that it accurately reflects the diverse perspectives within the U.S.
+electorate.
+The dataset employs a matched random sampling methodology, with its representativeness further confirmed through a two-stage weighting process involving entropy balancing and iterative proportional fitting.
+Preprocessing steps, including sample matching, weighting, and vote validation, are conducted to ensure data quality and representativeness, thereby minimizing the risk of representative bias.
+
+To better understand the American election and its voting system that occurred in 2022, we need to follow these steps:
+
+Define the population: The survey involves 60,000 cases, based on the survey of adult participants in the fall of 2022.
+Individual respondents participate in the survey, which is designed to record various information related to electoral behavior, political perspectives, and demographic characteristics.
+
+Gather Data: Acquire information regarding the total number of confirmed survey cases.
+This dataset should include various factors such as,  election experiences, contextual data, demographic details (e.g., gender, race, education), political affiliations, and viewpoints on diverse policy matters.
+
+Determine the Time Period: Specify the time frame to calculate when the survey object was collected.
+The timeframe is relevant to survey participants about their opinions, voting intentions in the 2022 election.
+The first period is the pre-election data collection that occurred from September 29 to November 8, 2022, and the second period is post- election data gathered from November 10 to December 15, 2022.
+
+Calculate the Case: Calculate each individual's distribution to the survey object. And consider the outcome that will be given with the distributions.
 

### 2024-03-12 scripts/00-simulate_data.R
Update 00-simulate_data.R

@@ -1,8 +1,8 @@
 #### Preamble ####
 # Purpose: Simulates... [...UPDATE THIS...]
-# Author: Yang Zhou & Yuean Wang [...UPDATE THIS...]
+# Author: Yang Zhou & Yuean Wang & Dong Jun Yoon [...UPDATE THIS...]
 # Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Contact: cocoyang.zhou@utoronto.ca & dongjun.yoon@mail.utoronto.ca & yuean.wang@mail.utoronto.ca [...UPDATE THIS...]
 # License: MIT
 # Pre-requisites: [...UPDATE THIS...]
 # Any other information needed? [...UPDATE THIS...]

### 2024-03-12 paper/datasheet_template.qmd
Update datasheet_template.qmd

--- 2024-03-10 paper/datasheet_template.qmd
@@
   - Yuean Wang
-thanks: "Code and data are available at: LINK."
+  - Dong Jun Yoon
+thanks: "Code and data are available at: <https://github.com/yangzhoucoco/Political-support-in-the-United-States.git.>"
 date: "`09 March 2024`"

### 2024-03-12 paper/paper.qmd
Update paper.qmd

@@
   - Dong Jun Yoon
-  - Another author
+  - Yang Zhou
+  - Yuean Wang
 thanks: "Code and data are available at: <https://github.com/yangzhoucoco/Political-support-in-the-United-States.git>."

### 2024-03-12 paper/paper.qmd
Update paper.qmd

--- 2024-03-12 paper/paper.qmd
@@
 ---
-title: "My title"
-subtitle: "My subtitle if needed"
+title: "Political-support-in-the-United-States"
+
 author: 
   - Dong Jun Yoon
-  - Another author
+  - Yang Zhou
+  - Yuean Wang
 thanks: "Code and data are available at: <https://github.com/yangzhoucoco/Political-support-in-the-United-States.git>."
-date: today
+date: March 12, 2024
 date-format: long

### 2024-03-12 scripts/00-simulate_data.R
Update 00-simulate_data.R

@@ -1,11 +1,11 @@
 #### Preamble ####
 # Purpose: Simulates... [...UPDATE THIS...]
 # Author: Yang Zhou & Yuean Wang & Dong Jun Yoon [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
+# Date: 12 February 2023 [...UPDATE THIS...]
 # Contact: cocoyang.zhou@utoronto.ca & dongjun.yoon@mail.utoronto.ca & yuean.wang@mail.utoronto.ca [...UPDATE THIS...]
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: No
+# Any other information needed? No
 
 
 #### Workspace setup ####

### 2024-03-12 scripts/01-download_data.R
Update 01-download_data.R

@@ -4,8 +4,8 @@
 # Date: 11 February 2023 [...UPDATE THIS...]
 # Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: No
+# Any other information needed? No
 
 
 #### Workspace setup ####

### 2024-03-12 scripts/00-simulate_data.R
Update 00-simulate_data.R

@@ -1,8 +1,8 @@
 #### Preamble ####
-# Purpose: Simulates... [...UPDATE THIS...]
-# Author: Yang Zhou & Yuean Wang & Dong Jun Yoon [...UPDATE THIS...]
-# Date: 12 February 2023 [...UPDATE THIS...]
-# Contact: cocoyang.zhou@utoronto.ca & dongjun.yoon@mail.utoronto.ca & yuean.wang@mail.utoronto.ca [...UPDATE THIS...]
+# Purpose: Simulates... 
+# Author: Yang Zhou & Yuean Wang & Dong Jun Yoon 
+# Date: 12 February 2023 
+# Contact: cocoyang.zhou@utoronto.ca & dongjun.yoon@mail.utoronto.ca & yuean.wang@mail.utoronto.ca 
 # License: MIT
 # Pre-requisites: No
 # Any other information needed? No

### 2024-03-12 scripts/01-download_data.R
Update 01-download_data.R

@@ -1,8 +1,8 @@
 #### Preamble ####
 # Purpose: Downloads and saves the data from [...UPDATE THIS...]
 # Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Date: 12 March 2024 
+# Contact: cocoyang.zhou@utoronto.ca & dongjun.yoon@mail.utoronto.ca & yuean.wang@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: No
 # Any other information needed? No

### 2024-03-12 scripts/01-download_data.R
Update 01-download_data.R

@@ -1,6 +1,6 @@
 #### Preamble ####
 # Purpose: Downloads and saves the data from [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
+# Author: Yang Zhou & Yuean Wang & Dong Jun Yoon 
 # Date: 12 March 2024 
 # Contact: cocoyang.zhou@utoronto.ca & dongjun.yoon@mail.utoronto.ca & yuean.wang@mail.utoronto.ca
 # License: MIT

### 2024-03-12 scripts/00-simulate_data.R
Update 00-simulate_data.R

@@ -1,7 +1,7 @@
 #### Preamble ####
 # Purpose: Simulates... 
 # Author: Yang Zhou & Yuean Wang & Dong Jun Yoon 
-# Date: 12 February 2023 
+# Date: 12 March 2024
 # Contact: cocoyang.zhou@utoronto.ca & dongjun.yoon@mail.utoronto.ca & yuean.wang@mail.utoronto.ca 
 # License: MIT
 # Pre-requisites: No

### 2024-03-12 scripts/02-data_cleaning.R
Update 02-data_cleaning.R

@@ -1,11 +1,11 @@
 #### Preamble ####
 # Purpose: Cleans the raw plane data recorded by two observers..... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 6 April 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Author: Yang Zhou & Yuean Wang & Dong Jun Yoon 
+# Date: 12 March 2024 
+# Contact: cocoyang.zhou@utoronto.ca & dongjun.yoon@mail.utoronto.ca & yuean.wang@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: No
+# Any other information needed? No
 
 #### Workspace setup ####
 library(tidyverse)

### 2024-03-12 scripts/03-test_data.R
Update 03-test_data.R

@@ -1,11 +1,11 @@
 #### Preamble ####
 # Purpose: Tests... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Author: Yang Zhou & Yuean Wang & Dong Jun Yoon 
+# Date: 12 March 2024 
+# Contact: cocoyang.zhou@utoronto.ca & dongjun.yoon@mail.utoronto.ca & yuean.wang@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: No
+# Any other information needed? No
 
 
 #### Workspace setup ####

### 2024-03-12 scripts/04-model.R
Update 04-model.R

@@ -1,11 +1,11 @@
 #### Preamble ####
 # Purpose: Models... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Author: Yang Zhou & Yuean Wang & Dong Jun Yoon 
+# Date: 12 March 2024 
+# Contact: cocoyang.zhou@utoronto.ca & dongjun.yoon@mail.utoronto.ca & yuean.wang@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: No
+# Any other information needed? No
 
 
 #### Workspace setup ####

### 2024-03-12 paper/paper.qmd
Update paper.qmd

@@
 thanks: "Code and data are available at: <https://github.com/yangzhoucoco/Political-support-in-the-United-States.git>."
-date: March 12, 2024
+date: today
 date-format: long

### 2024-03-12 paper/paper.qmd
Update paper.qmd

@@
 
-Talk more about it.
-
-And also planes (@fig-vote).
-(You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)
-
-Talk way more about it.
-
 # Model
@@
 We run the model in R [@citeR] using the `rstanarm` package of @rstanarm, `here` package of @here and `model_summary` package of @model_summary, we use the default priors from `rstanarm`
+
+Through feature selection, the influence of redundant features and noise features is reduced, and the generalization ability of the model is improved.
+By means of L1 regularization and L2 regularization, the complexity of the model is limited and overfitting is prevented.
+By integrating the results of multiple classifiers, the accuracy and robustness of the model are improved.
+By changing the structure of the model, such as increasing the depth of the network, increasing the hidden layer and changing the activation function, the expressibility of the model is improved.
+By expanding, rotating and scaling the data, the diversity of the data is increased and the generalization ability of the model is improved.
 

### 2024-03-12 paper/paper.qmd
Update paper.qmd

@@
 ---
-title: "Political-support-in-the-United-States"
-
+title: "Datasheet for 'A dataset'"
 author: 
-  - Dong Jun Yoon
   - Yang Zhou
   - Yuean Wang
-thanks: "Code and data are available at: <https://github.com/yangzhoucoco/Political-support-in-the-United-States.git>."
+  - Dong Jun Yoon
+thanks: "Code and data are available at: <https://github.com/yangzhoucoco/Political-support-in-the-United-States.git.>"
 date: today
 date-format: long
-abstract: 
-There is no other nation in the world that conducts elections the way the United States does.
+abstract: "There is no other nation in the world that conducts elections the way the United States does.
 Local government representatives oversee elections in around 8,000 distinct jurisdictions.
@@
 These distinguishing characteristics of our voting system contribute to the issues seen in the most recent elections.
-This paper is mainly based on the 2022 US election.
+This paper is mainly based on the 2022 US election."
 format: pdf
@@
 # Model
-
-The goal of our modelling strategy is twofold. Firstly,...
-
-Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].
-
 ## Model set-up

### 2024-03-12 paper/paper.qmd
Update paper.qmd

@@
 ---
-title: "Datasheet for 'A dataset'"
+title: "Political Support in the United-States'"
 author: 

### 2024-03-12 paper/paper.qmd
Update paper.qmd

--- 2024-03-12 paper/paper.qmd
@@
 ---
-title: "Datasheet for 'A dataset'"
+title: "Political Support in the United States'"
 author: 

### 2024-03-12 paper/paper.qmd
Update paper.qmd

--- 2024-03-12 paper/paper.qmd
@@
 ---
-title: "Datasheet for 'A dataset'"
+title: "Political Support in the United States'"
 author: 
+  - Dong Jun Yoon
+  - Yuean Wang
   - Yang Zhou
-  - Yuean Wang
-  - Dong Jun Yoon
 thanks: "Code and data are available at: <https://github.com/yangzhoucoco/Political-support-in-the-United-States.git.>"

### 2024-03-12 paper/paper.qmd
Update paper.qmd

@@
 
-## application of Logistic regression {#sec-first-point}
+# Discussion
+
+## Application of Logistic Regression {#sec-first-point}
 Logistic regression is also known as generalized linear regression model, and its form is basically the same as that of linear regression model.
@@
 
-## linear regression model
+## Linear Regression Model
 In summary, the essence of logistic regression model is to transform the linear regression model Q through a nonlinear Sigmoid function to obtain a probability value between 0 and 1.
@@
 
-## model building
+## Model Building
 The training set is used to train the data and build the model, and the test set is used to check the effect of the model built after training.
@@
 
-## Weaknesses and next steps
+## Weaknesses and Next Steps
 

### 2024-03-14 paper/datasheet.qmd
Update and rename

--- 2024-03-10 paper/datasheet_template.qmd
@@
 author: 
+  - Dong Jun Yoon
+  - Yuean Wang
   - Yang Zhou
-  - Yuean Wang
-thanks: "Code and data are available at: LINK."
+thanks: "Code and data are available at: <https://github.com/yangzhoucoco/Political-support-in-the-United-States.git.>"
 date: "`09 March 2024`"

### 2024-03-15 paper/paper.qmd
Update paper.qmd

@@
 date-format: long
-abstract: "There is no other nation in the world that conducts elections the way the United States does.
-Local government representatives oversee elections in around 8,000 distinct jurisdictions.
-They are then under the general supervision of authorities, who are frequently selected through election procedures or partisan appointees.
-Typically, the voter liaison at the polling place is a temporary worker who works unpaid for a single day and only gets a few hours of training.
-These distinctive characteristics of our electoral system, along with the fact that Americans vote more frequently than citizens in other countries on a wider range of issues and positions, create special difficulties for the efficient administration of elections that voters across demand and deserve.
-None of the other nations' electoral systems display all or any of these traits, but none have the same mix of US administrative traits.
-The quality of administration differs from jurisdiction to jurisdiction and even from polling place to polling place because of decentralization and dependence on volunteers.
-Because partisan officials will be involved, accusations of partisanship regarding the rules or their interpretation may arise based on the outcome of the judgments made by the officials and who stands to gain from it.
-The quantity and variety of democratic options in protracted elections have outpaced voters' attention spans and cognitive capacities.
-These distinguishing characteristics of our voting system contribute to the issues seen in the most recent elections.
-This paper is mainly based on the 2022 US election."
+abstract: "This paper examines the unique characteristics of the United States' election system and their impact on the administration of elections.
+Throughout an analysis of the 2022 US election, it was found that the decentralization, reliance on volunteers, and frequent voting cycles pose significant challenges to efficient election management.
+These challenges result in inconsistencies in administration quality and raise concerns about partisanship.
+Understanding these complexities is significant since it allows people to recognize the challenges faced in modern democratic processes and for conducting improvements in election administration worldwide."
+
 format: pdf

### 2024-03-15 paper/paper.qmd
Update paper.qmd

@@
 library(here)
+library(modelsummary)
+library(knitr)
+library(kableExtra)
+library(readr)
+library(ggplot2)
 ```
@@
       )
-ces2022
+
+ces2022_table <- ces2022 |>
+  kable("html", booktabs = TRUE, caption = "Brief summary of variables types") |>
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)
+
+print(ces2022_table)
 ```
+
    After downloading @dataverse, We using @get_dataframe_by_name to access the CES.
@@
 
+library(ggplot2)
+library(readr)
+library(here)
+
 ces2022 <- read_csv(here("data/analysis_data/analysis_data.csv"))
 
-ces2022 |>
-  ggplot(aes(x = race, fill = voted_for)) +
-  stat_count(position = "dodge") +
-  geom_text(stat='count', aes(label=..count..), position=position_dodge(width=0.9), vjust=-0.25, color="black") +
+ggplot(data = ces2022, aes(x = race, fill = voted_for)) +
+  geom_bar(position = "dodge") +  
+  geom_text(
+    aes(label = ..count..),
+    stat = 'count',
+    position = position_dodge(width = 0.9),
+    vjust = -0.25,
+    color = "black",
+    size = 3  
+  ) +
   facet_wrap(facets = vars(gender4)) +
-  theme_minimal() +
+  theme_minimal(base_size = 14) +  
   labs(
@@
   scale_fill_brewer(palette = "Set1") +
-  theme(legend.position = "bottom")
+  theme(
+    legend.position = "bottom",
+    strip.text = element_text(size = 12)  
+  )
+
 ```
+
 The collected dataset from the Cooperative Election Study (CES) offers a comprehensive view of U.S.
 adult citizens' electoral behaviors, political opinions, and demographic characteristics.
-The CES 2022 dataset, gathered through an online survey by YouGov, encompasses 60,000 instances, meticulously detailed and categorized by various factors such as election experiences, contextual data, demographic information (e.g., gender, race, education), political affiliations, and opinions on various policy issues.
+The CES 2022 dataset, gathered through an online survey by YouGov, encompasses 60,000 instances, meticulously detailed and categorized by various factors such as election experiences, contextual data, demographic information (e.g., gender and race), political affiliations, and opinions on various policy issues.
 This dataset ensures a reliable representation of the population through its meticulous sampling methodology and validation processes, guaranteeing that it accurately reflects the diverse perspectives within the U.S.
@@
 Gather Data: Acquire information regarding the total number of confirmed survey cases.
-This dataset should include various factors such as,  election experiences, contextual data, demographic details (e.g., gender, race, education), political affiliations, and viewpoints on diverse policy matters.
+This dataset should include various factors such as,  election experiences, contextual data, demographic details, political affiliations, and viewpoints on diverse policy matters.
 
@@
 # Results
-
 Our results are summarized in @tbl-modelresults.Logistic regression is a common classification algorithm used to predict binary classification problems.
@@
 #| eval: true
-#| label: tbl-modelresults
-#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
 #| warning: false
+#| message: false
 

### 2024-03-16 paper/paper.qmd
Update paper.qmd

@@
 # Introduction
+Introduction:
+
 The goal of the Cooperative Election Study (CES) is to investigate how Americans vote and perceive their electoral experiences, how they hold their representatives accountable in elections, and how their behavior and experiences vary depending on the political climate and social milieu.
-The study used an extremely large sample that allowed it to account for variations across different legislative districts.
-Actually, the sample size at the state level is sufficient to measure the voter preference distribution within the majority of states with a respectable degree of accuracy.
-60 teams participated in 2022CES, which resulted in a 60,000-case generic content sample. 
-Fall of 2022 saw the recruitment of study participants.
-Every research team invested in a 1,000-person nationwide sample survey from Redwood City, California-based YouGov.
-Two waves of interviewing were used for the 2022 survey.
+The Cooperative Election Study (CES) serves as a crucial platform for understanding the complexities of American electoral systems.
+This paper delves into the findings of the 2022 CES, which aimed to provide insights into voter behavior, perceptions of electoral experiences, and the broader socio-political milieu shaping democratic governance.
+With a focus on exploring how Americans vote, perceive their electoral experiences, and navigate the political climate, the CES helps us in understanding the electoral outcomes in the United States.
+
+The Cooperative Election Study (CES) addressed gaps in understanding voter behavior by employing a multifaceted approach involving 60,000 cases and 60 research teams.
+Their methods included pre-election surveys and post-election assessments, providing detailed insights into American elections.
 Pre-election surveys were filled out on the spot between September 29 and November 8.
-The post-election campaigning frenzy took place between November 10 and December 15.
+The Post-election campaigning frenzy took place between November 10 and December 15.
 For every 1,000 respondents, half of the questions had common material while the other half were fully created and managed by each study team.
@@
 The project built upon the analysis conducted by the Public Opinion Research and Training Lab at the Massachusetts Institute of Technology in 2005.
+
+Understanding these findings is crucial for policymakers, researchers, and citizens, as they shed light on the complexities of democracy and provide insights to strengthen democratic institutions.
+This paper aims to dive deeper into the CES findings, analyzing their implications for the future of American democracy.
 

### 2024-03-16 paper/paper.qmd
Update paper.qmd

@@
 # Introduction
-Introduction:
 
@@
 The project built upon the analysis conducted by the Public Opinion Research and Training Lab at the Massachusetts Institute of Technology in 2005.
-
 Understanding these findings is crucial for policymakers, researchers, and citizens, as they shed light on the complexities of democracy and provide insights to strengthen democratic institutions.
 This paper aims to dive deeper into the CES findings, analyzing their implications for the future of American democracy.
+
+The data utilized for analysis, including both survey and census data, is in Section 2.
+Following that, Section 3 introduces the model designed to generalize patterns and forecast election outcomes.
+I will also talk about the predicted results derived from the model in Section 4.
+Lastly, Section 5 contains the results in a broader context and addresses weaknesses of this paper as well as the future explorations.
+This paper uses the programming language R (R Core Team 2022).
+The analysis, the model and the visualizations use the following packages: ipumsr (Greg Freedman Ellis, Derek Burk, and Finn Roberts 2024), dplyr (Wickham et al.
+2023), readr (Wickham, Hester, and Bryan 2024), tidyr (Wickham, Vaughan, and Girlich 2024), arrow (Richardson et al.
+2024), ggplot2 (Wickham 2016), knitr (Xie 2014), statebins (Rudis 2020), modelsi (Arel-Bundock 2022), broom (Robinson, Hayes, and Couch 2023), here (Müller 2020), and kableExt
+2024).
 

### 2024-03-16 paper/paper.qmd
Update paper.qmd

@@
 # Discussion
-
-# Discussion
-
 ## Application of Logistic Regression {#sec-first-point}

### 2024-03-16 paper/paper.qmd
Update paper.qmd

@@
 # Introduction
-
 The goal of the Cooperative Election Study (CES) is to investigate how Americans vote and perceive their electoral experiences, how they hold their representatives accountable in elections, and how their behavior and experiences vary depending on the political climate and social milieu.
@@
 
-The data utilized for analysis, including both survey and census data, is in Section 2.
+Throughout the paper, the data utilized for analysis, including both survey and census data, is in Section 2.
 Following that, Section 3 introduces the model designed to generalize patterns and forecast election outcomes.

### 2024-03-16 paper/paper.qmd
Update paper.qmd

@@
 2023), readr (Wickham, Hester, and Bryan 2024), tidyr (Wickham, Vaughan, and Girlich 2024), arrow (Richardson et al.
-2024), ggplot2 (Wickham 2016), knitr (Xie 2014), statebins (Rudis 2020), modelsi (Arel-Bundock 2022), broom (Robinson, Hayes, and Couch 2023), here (Müller 2020), and kableExt
-2024).
+2024), ggplot2 (Wickham 2016), knitr (Xie 2014), statebins (Rudis 2020), modelsi (Arel-Bundock 2022), broom (Robinson, Hayes, and Couch 2023), here (Müller 2020), and kableExt 2024).
 
@@
 
-### Sampling and Sampling Matching
+## Sampling and Sampling Matching
 The CES 2022 dataset is a sample of adult U.S.
@@
 
-### Weightening
+## Weightening
 A weighting process is used to account for any residual imbalances between the matched samples, therefore rigorously verifying the representativeness of CES samples.
@@
 
-### Vote Vaildation
+## Vote Vaildation
 The CES incorporated vote validation to verify the accuracy of respondents’ reported voting behaviors.
@@
 
-   After downloading @dataverse, We using @get_dataframe_by_name to access the CES.
-We select and save the data that we are most care about, which are "votereg", "presvote20post", "race", and "gender4".
-"votereg" represent the voter registration status.
-To be more specific, whether they are registered to vote or not.
-"presvote20post" records the president that voter select in the election of 2020.
-“race" describe the voter's raical or ethnic group, and "gender4" refer to the gender of voters.
-  However, when we access the raw data, there are some variables that we are not interested in.
-Therefore, we use the codebook to delve into the details.
-We only care about the voter who are registered to vote, and we are mainly focus on investigating the voter who select Biden or Trump in 2020.
-We found out that when the "presvote20post" is 1, then this indicates the register vote for Biden, and when it is 2 represents that the voter stand for Trump.
-We use @tidyverse to filter to the voters that we care about and label them with meaningful title.
-In addition，CES also provide the information for the gender of the voter.
-However, we noticed that there are four types of gender, which are man, woman, non-binary, other, and none and we are more interested in the group of man and woman.
-Therefore, we filter the gender by using @tidyverse.
-When the variable "gender" is 1, this indicates "man", but we rename all "man" to "male".
-When the variable "gender" is 2, it refers to "woman".
-We also rename all "woman" to "female".
-Finally, the codebook also define different "race" from 1 to 8, which are White, Black, Hispanic, Asian, Native American, Middle Eastern, Two or more races, and other.
-We keep all those races because we are not only interested in the major racial group, but also curious about the respond from minority group.
-  To better understand the raw data, a summary table had been drawn in order to provide more details for each variables, explaining the variables we select.
-
-## Measurements
 ```{r}
@@
 ```
+   After downloading @dataverse, We using @get_dataframe_by_name to access the CES.
+We select and save the data that we are most care about, which are "votereg", "presvote20post", "race", and "gender4".
+"votereg" represent the voter registration status.
+To be more specific, whether they are registered to vote or not.
+"presvote20post" records the president that voter select in the election of 2020.
+“race" describe the voter's raical or ethnic group, and "gender4" refer to the gender of voters.
+  However, when we access the raw data, there are some variables that we are not interested in.
+Therefore, we use the codebook to delve into the details.
+We only care about the voter who are registered to vote, and we are mainly focus on investigating the voter who select Biden or Trump in 2020.
+We found out that when the "presvote20post" is 1, then this indicates the register vote for Biden, and when it is 2 represents that the voter stand for Trump.
+We use @tidyverse to filter to the voters that we care about and label them with meaningful title.
+In addition，CES also provide the information for the gender of the voter.
+However, we noticed that there are four types of gender, which are man, woman, non-binary, other, and none and we are more interested in the group of man and woman.
+Therefore, we filter the gender by using @tidyverse.
+When the variable "gender" is 1, this indicates "man", but we rename all "man" to "male".
+When the variable "gender" is 2, it refers to "woman".
+We also rename all "woman" to "female".
+Finally, the codebook also define different "race" from 1 to 8, which are White, Black, Hispanic, Asian, Native American, Middle Eastern, Two or more races, and other.
+We keep all those races because we are not only interested in the major racial group, but also curious about the respond from minority group.
+  To better understand the raw data, a summary table @fig-variables had been drawn in order to provide more details for each variables, explaining the variables we select.
+We select race and gender as the key variables that related to voter behavior.
+In @fig-vote, we can find the support data for both Biden and Trump based on the variables of gender and race.
 
+## Measurements 
 The collected dataset from the Cooperative Election Study (CES) offers a comprehensive view of U.S.
@@
 
-# Model
+# Model {#sec-model}
 ## Model set-up
@@
 
-### Model justification
+## Model justification
 
@@
 
-# Results
-Our results are summarized in @tbl-modelresults.Logistic regression is a common classification algorithm used to predict binary classification problems.
+# Results {#sec-results}
+Our results are summarized in @tbl-model-summary-table.Logistic regression is a common classification algorithm used to predict binary classification problems.
 In logistic regression, the probability that a sample belongs to a certain class is determined by mapping the input data to a probability range between 0 and 1 using a logical function, such as the sigmoid function.
@@
 #| echo: false
-#| eval: true
+#| message: false
 #| warning: false
-#| message: false
+#| label: tbl-model-summary-table
+#| tbl-cap: "Explanatory models of political preferences based on gender and race (n = 500)"
 
@@
 
-# Discussion
-## Application of Logistic Regression {#sec-first-point}
+# Discussion {#sec-Discussion}
+
+## Application of Logistic Regression 
 Logistic regression is also known as generalized linear regression model, and its form is basically the same as that of linear regression model.
@@
 
-# References
+# References {#sec-Reference}

### 2024-03-16 paper/paper.qmd
Update paper.qmd

@@
 
-Throughout the paper, the data utilized for analysis, including both survey and census data, is in Section 2.
+Throughout the paper, the data utilized for analysis, including both survey and census data, measurements, is in Section 2.
 Following that, Section 3 introduces the model designed to generalize patterns and forecast election outcomes.
-I will also talk about the predicted results derived from the model in Section 4.
-Lastly, Section 5 contains the results in a broader context and addresses weaknesses of this paper as well as the future explorations.
+It will talk about how the model is set up and model justification.
+In Section 4, I will talk about the predicted results derived from the model, this includes the result of the model.
+Lastly, Section 5 contains more detailed results in a broader context and addresses weaknesses of this paper as well as the future explorations.
 This paper uses the programming language R (R Core Team 2022).
@@
 2023), readr (Wickham, Hester, and Bryan 2024), tidyr (Wickham, Vaughan, and Girlich 2024), arrow (Richardson et al.
-2024), ggplot2 (Wickham 2016), knitr (Xie 2014), statebins (Rudis 2020), modelsi (Arel-Bundock 2022), broom (Robinson, Hayes, and Couch 2023), here (Müller 2020), and kableExt 2024).
+2024), ggplot2 (Wickham 2016), knitr (Xie 2014), statebins (Rudis 2020), modelsi (Arel-Bundock 2022), broom (Robinson, Hayes, and Couch 2023), here (Müller 2020), and kableExt
+2024).
 
@@
 
-Define the population: The survey involves 60,000 cases, based on the survey of adult participants in the fall of 2022.
+**Define the Population:** The survey involves 60,000 cases, based on the survey of adult participants in the fall of 2022.
 Individual respondents participate in the survey, which is designed to record various information related to electoral behavior, political perspectives, and demographic characteristics.
 
-Gather Data: Acquire information regarding the total number of confirmed survey cases.
+**Gather Data:** Acquire information regarding the total number of confirmed survey cases.
 This dataset should include various factors such as,  election experiences, contextual data, demographic details, political affiliations, and viewpoints on diverse policy matters.
 
-Determine the Time Period: Specify the time frame to calculate when the survey object was collected.
+**Determine the Time Period:** Specify the time frame to calculate when the survey object was collected.
 The timeframe is relevant to survey participants about their opinions, voting intentions in the 2022 election.
@@
 
-Calculate the Case: Calculate each individual's distribution to the survey object. And consider the outcome that will be given with the distributions.
+**Calculate the Case:** Calculate each individual's distribution to the survey object. And consider the outcome that will be given with the distributions.
 

### 2024-03-16 paper/paper.qmd
Update paper.qmd

@@
 format: pdf
+toc: true
 number-sections: true
@@
 # Results {#sec-results}
-Our results are summarized in @tbl-model-summary-table.Logistic regression is a common classification algorithm used to predict binary classification problems.
+Our results are summarized in @tbl-model-summary-tableLogistic regression is a common classification algorithm used to predict binary classification problems.
 In logistic regression, the probability that a sample belongs to a certain class is determined by mapping the input data to a probability range between 0 and 1 using a logical function, such as the sigmoid function.

### 2024-03-16 paper/paper.qmd
Update paper.qmd

@@
 
+## Findings
+In this paper, the 2022 Cooperative Election Study (CES) was used for understanding the complexities of American electoral systems which was discussed in Section 2.
+In section 3, we applied a Bayesian logistic regression model to know if a person is likely to support Biden, based on their gender, race, and education status.
+In section 4, we discussed the summarization of the major results based on the research we did in Section 2 and 3.
+Summarization of our major results:
+
+Males are less likely to support Biden than Females,
+Women most likely to vote for Biden,
+Middle Eastern, Hispanic, Black and Asian individuals are more likely to vote and show support for Biden.
+
+Throughout the discussion part, we will now provide detailed points of our results in the following sections.
+
 ## Application of Logistic Regression 

### 2024-03-16 paper/paper.qmd
Update paper.qmd

@@
 
-Males are less likely to support Biden than Females,
-Women most likely to vote for Biden,
-Middle Eastern, Hispanic, Black and Asian individuals are more likely to vote and show support for Biden.
+1.Males are less likely to support Biden than Females,
+2.Women most likely to vote for Biden,
+3.Middle Eastern, Hispanic, Black and Asian individuals are more likely to vote and show support for Biden.
 
 Throughout the discussion part, we will now provide detailed points of our results in the following sections.
+
+## Middle Eastern, Hispanic, Black and Asian individuals are more likely to vote and show support for Biden.
+
+Based on the analysis of Figure 1 which is located under 2.3 Measurement, we can find out that Middle Eastern, Hispanic, Black and Asian individuals are more likely to vote and show support for Biden.
+In the graph we provided, we can easily tell that votes for Biden are higher than votes for Trump for certain races.
+For example, Black individuals have a total vote of 5293 individuals for Biden, however only 642 individuals support and vote for Trump.
+This same trend can also be observed in races such as Middle Eastern, Hispanic, Black and Asian individuals.
 

### 2024-03-17 paper/paper.qmd
Update paper.qmd

@@
 
-1.Males are less likely to support Biden than Females,
-2.Women most likely to vote for Biden,
-3.Middle Eastern, Hispanic, Black and Asian individuals are more likely to vote and show support for Biden.
+1.Males are less likely to support Biden than Females,women most likely to vote for Biden,
+2.Middle Eastern, Hispanic, Black and Asian individuals are more likely to vote and show support for Biden.
 

### 2024-03-17 paper/paper.qmd
Update paper.qmd

@@
 
+## Males are less likely to support Biden than Females, women most likely to vote for Biden.
+
+Based on the analysis of Figure 1, located under 2.3 Measurement, we can infer that males (represented by 1) exhibit a lower propensity to support Biden compared to females (represented by 2).
+Throughout most of the race, 1 consistently has fewer votes than 2.
+Specifically, women are identified as the demographic most inclined to vote for Biden, indicating a notable gender disparity in political preferences favoring the Biden candidacy.
+
 ## Middle Eastern, Hispanic, Black and Asian individuals are more likely to vote and show support for Biden.

### 2024-03-17 paper/paper.qmd
Update paper.qmd

@@
 
+In this paper, we performed a logistic regression model from our cleaned dataset, which analysis 500 observations.
+Our focus of this paper was relationship of presidential candidate voted by individuals between the races (raceBlack, raceHispanic, raceMiddle Eastern, raceNative American, raceOther, raceTwo or more races, raceWhite) and the reference group, raceAsian.
+
 ```{r}
@@
 ```
+The coefficient represents the logarithm of the anticipated variance in backing for Biden in contrast to Trump.
+When the coefficient values are negative, which means the voters decrease their support in Biden.
+Whereas, when the values are greater and equal to zero (positive) meaning the voters increase their support for Biden.
+
+From the @tbl-model-summary-tableLogistic, with the constant variable, raceAsian, the intercept is -0.462 which means that the support for Biden decreases by about 0.784 units while all other variables remain the same.
+The following race, Hispanic (0.354), Middle Eastern (0.535), White (0.940), Native American (1.245), Two or more races (1.372) has stronger/ increasing their support for stronger/ increasing their support for Biden; in this case, the mixed race people have the strongest support for Biden.
+Yet, Black (−1.030) and Other  (−0.092) decrease support for Biden by looking at the coefficients.
 

### 2024-03-17 paper/paper.qmd
Update paper.qmd

@@
 Specifically, women are identified as the demographic most inclined to vote for Biden, indicating a notable gender disparity in political preferences favoring the Biden candidacy.
+This trend is very recognizable based on research: women are registered to vote in the U.S.
+at higher rates than men.
+In recent years, the number of women registered to vote in the U.S.
+has typically been about 10 million more than the number of men registered to vote.
+In every presidential election since 1980, the proportion of eligible female adults who voted has exceeded the proportion of eligible male adults who voted.
+In all presidential elections prior to 1980, the voter turnout rate for women was lower than the rate for men.
+The number of female voters has exceeded the number of male voters in every presidential election since 1964.
+https://cawp.rutgers.edu/facts/voters/gender-differences-voter-turnout#GGN
 

### 2024-03-17 paper/paper.qmd
Update paper.qmd

@@
 Specifically, women are identified as the demographic most inclined to vote for Biden, indicating a notable gender disparity in political preferences favoring the Biden candidacy.
-This trend is very recognizable based on research: women are registered to vote in the U.S.
+This trend is very recognizable based on research @Misc: women are registered to vote in the U.S.
 at higher rates than men.
@@
 The number of female voters has exceeded the number of male voters in every presidential election since 1964.
-https://cawp.rutgers.edu/facts/voters/gender-differences-voter-turnout#GGN
 
@@
 
-Based on the analysis of Figure 1 which is located under 2.3 Measurement, we can find out that Middle Eastern, Hispanic, Black and Asian individuals are more likely to vote and show support for Biden.
+Based on the analysis of Figure 1, located under 2.3 Measurement, we can find out that Middle Eastern, Hispanic, Black and Asian individuals are more likely to vote and show support for Biden.
 In the graph we provided, we can easily tell that votes for Biden are higher than votes for Trump for certain races.
@@
 This same trend can also be observed in races such as Middle Eastern, Hispanic, Black and Asian individuals.
+Additionally, in recent elections @Misc, among Asian American/Pacific Islander, Black, Hispanic, and white voters, the number of women voters has exceeded the number of male voters.
+The gender gap in voter turnout rates is the largest for Black voters.
+Women have also voted at higher rates than men among Hispanic and white voters in all presidential elections since the 1980s.
+Among Asian American/Pacific Islander voters, there is no consistent gender gap in voter turnout.
 

### 2024-03-17 paper/paper.qmd
Update paper.qmd

@@
 Specifically, women are identified as the demographic most inclined to vote for Biden, indicating a notable gender disparity in political preferences favoring the Biden candidacy.
-This trend is very recognizable based on research @Misc: women are registered to vote in the U.S.
+This trend is very recognizable based on research: women are registered to vote in the U.S.
 at higher rates than men.
@@
 This same trend can also be observed in races such as Middle Eastern, Hispanic, Black and Asian individuals.
-Additionally, in recent elections @Misc, among Asian American/Pacific Islander, Black, Hispanic, and white voters, the number of women voters has exceeded the number of male voters.
+Additionally, in recent elections, among Asian American/Pacific Islander, Black, Hispanic, and white voters, the number of women voters has exceeded the number of male voters.
 The gender gap in voter turnout rates is the largest for Black voters.

### 2024-03-17 paper/paper.qmd
Update paper.qmd

@@
 
-Based on the analysis of Figure 1, located under 2.3 Measurement, we can infer that males (represented by 1) exhibit a lower propensity to support Biden compared to females (represented by 2).
+Based on the analysis of Figure 1: The distribution of presidential preferences, by gender and race, located under 2.3 Measurement, we can infer that males (represented by 1) exhibit a lower propensity to support Biden compared to females (represented by 2).
 Throughout most of the race, 1 consistently has fewer votes than 2.
@@
 
-Based on the analysis of Figure 1, located under 2.3 Measurement, we can find out that Middle Eastern, Hispanic, Black and Asian individuals are more likely to vote and show support for Biden.
+Based on the analysis of Figure 1: The distribution of presidential preferences, by gender and race, located under 2.3 Measurement, we can find out that Middle Eastern, Hispanic, Black and Asian individuals are more likely to vote and show support for Biden.
 In the graph we provided, we can easily tell that votes for Biden are higher than votes for Trump for certain races.

### 2024-03-17 paper/paper.qmd
Update paper.qmd

--- 2024-03-17 paper/paper.qmd
@@
 
-Based on the analysis of Figure 1, located under 2.3 Measurement, we can infer that males (represented by 1) exhibit a lower propensity to support Biden compared to females (represented by 2).
+Based on the analysis of @fig-vote: The distribution of presidential preferences, by gender and race, located under 2.6 Measurement, we can infer that males (represented by 1) exhibit a lower propensity to support Biden compared to females (represented by 2).
 Throughout most of the race, 1 consistently has fewer votes than 2.
@@
 
-Based on the analysis of Figure 1, located under 2.3 Measurement, we can find out that Middle Eastern, Hispanic, Black and Asian individuals are more likely to vote and show support for Biden.
+Based on the analysis of @fig-vote: The distribution of presidential preferences, by gender and race, located under 2.6 Measurement, we can find out that Middle Eastern, Hispanic, Black and Asian individuals are more likely to vote and show support for Biden.
 In the graph we provided, we can easily tell that votes for Biden are higher than votes for Trump for certain races.

### 2024-03-17 paper/paper.qmd
Update paper.qmd

--- 2024-03-17 paper/paper.qmd
@@
 
-Based on the analysis of Figure 1, located under 2.3 Measurement, we can infer that males (represented by 1) exhibit a lower propensity to support Biden compared to females (represented by 2).
+Based on the analysis of @fig-vote, located under 2.6 Measurement, we can infer that males (represented by 1) exhibit a lower propensity to support Biden compared to females (represented by 2).
 Throughout most of the race, 1 consistently has fewer votes than 2.
@@
 
-Based on the analysis of Figure 1, located under 2.3 Measurement, we can find out that Middle Eastern, Hispanic, Black and Asian individuals are more likely to vote and show support for Biden.
+Based on the analysis of @fig-vote, located under 2.6 Measurement, we can find out that Middle Eastern, Hispanic, Black and Asian individuals are more likely to vote and show support for Biden.
 In the graph we provided, we can easily tell that votes for Biden are higher than votes for Trump for certain races.

### 2024-03-17 paper/paper.qmd
Update paper.qmd

@@
 
-Throughout the paper, the data utilized for analysis, including both survey and census data, measurements, is in Section 2.
-Following that, Section 3 introduces the model designed to generalize patterns and forecast election outcomes.
+Throughout the paper, the data utilized for analysis, including both survey and census data, measurements, is in {#sec-data}.
+Following that, {#sec-model} introduces the model designed to generalize patterns and forecast election outcomes.
 It will talk about how the model is set up and model justification.
-In Section 4, I will talk about the predicted results derived from the model, this includes the result of the model.
-Lastly, Section 5 contains more detailed results in a broader context and addresses weaknesses of this paper as well as the future explorations.
-This paper uses the programming language R (R Core Team 2022).
-The analysis, the model and the visualizations use the following packages: ipumsr (Greg Freedman Ellis, Derek Burk, and Finn Roberts 2024), dplyr (Wickham et al.
-2023), readr (Wickham, Hester, and Bryan 2024), tidyr (Wickham, Vaughan, and Girlich 2024), arrow (Richardson et al.
-2024), ggplot2 (Wickham 2016), knitr (Xie 2014), statebins (Rudis 2020), modelsi (Arel-Bundock 2022), broom (Robinson, Hayes, and Couch 2023), here (Müller 2020), and kableExt
-2024).
+In {#sec-results}, I will talk about the predicted results derived from the model, this includes the result of the model.
+Lastly, {#sec-Discussion} contains more detailed results in a broader context and addresses weaknesses of this paper as well as the future explorations.
+This paper uses the programming language `R`[@citeR] .
+The analysis, the model and the visualizations use the following packages: `dplyr`[@dplyr],  `tidyverse`[@tidyverse], `ggplot2`[@ggplot], `knitr` [@knitr],  `here` [@here] , and `kableExtra` [@kableExtra],`modelsummary`[@model_summary], and `rstanarm`[@rstanarm].
 
@@
 ## Source and Methodology
-The 2022 Cooperative Election Study (CES) (@main_data) involved significant data preprocessing, cleaning, and labeling efforts to ensure the quality and representativeness of the survey data.
+The 2022 Cooperative Election Study (CES) [@main_data] involved significant data preprocessing, cleaning, and labeling efforts to ensure the quality and representativeness of the survey data.
 These efforts are elaborated on through descriptions of sampling methodology, matching procedures, and weighting processes as outlined in the CES Guide 2022.
@@
 The sample was deliberately created to be a true reflection of the population of the United States and to capture the variations among the different legislative districts for in-depth examination in the majority of states.
-Through the Internet, YouGov conducted the CES 2022 survey.
+Through the Internet, YouGov [@yougov] conducted the CES 2022 survey.
 60,000 adults were interviewed between September and November 2022 (pre-election data) and November and December 2022 (post-election data) for the Common Opinion.
@@
 ```
-   After downloading @dataverse, We using @get_dataframe_by_name to access the CES.
-We select and save the data that we are most care about, which are "votereg", "presvote20post", "race", and "gender4".
-"votereg" represent the voter registration status.
+   After downloading `dataverse` [@dataverse], We using `get_dataframe_by_name` [@get_dataframe_by_name] to access the CES.
+We select and save the data that we are most care about, which are `votereg`, `presvote20post`, `race`, and `gender4`.
+`votereg` represent the voter registration status.
 To be more specific, whether they are registered to vote or not.
-"presvote20post" records the president that voter select in the election of 2020.
-“race" describe the voter's raical or ethnic group, and "gender4" refer to the gender of voters.
+`presvote20post` records the president that voter select in the election of 2020.
+“race" describe the voter's raical or ethnic group, and `gender4` refer to the gender of voters.
   However, when we access the raw data, there are some variables that we are not interested in.
@@
 We found out that when the "presvote20post" is 1, then this indicates the register vote for Biden, and when it is 2 represents that the voter stand for Trump.
-We use @tidyverse to filter to the voters that we care about and label them with meaningful title.
+We use `tidyverse` [@tidyverse] to filter to the voters that we care about and label them with meaningful title.
 In addition，CES also provide the information for the gender of the voter.
 However, we noticed that there are four types of gender, which are man, woman, non-binary, other, and none and we are more interested in the group of man and woman.
-Therefore, we filter the gender by using @tidyverse.
-When the variable "gender" is 1, this indicates "man", but we rename all "man" to "male".
+Therefore, we filter the gender by using `tidyverse` [@tidyverse].
+When the variable `gender` is 1, this indicates "man", but we rename all "man" to "male".
 When the variable "gender" is 2, it refers to "woman".
 We also rename all "woman" to "female".
-Finally, the codebook also define different "race" from 1 to 8, which are White, Black, Hispanic, Asian, Native American, Middle Eastern, Two or more races, and other.
+Finally, the codebook also define different `race` from 1 to 8, which are White, Black, Hispanic, Asian, Native American, Middle Eastern, Two or more races, and other.
 We keep all those races because we are not only interested in the major racial group, but also curious about the respond from minority group.
@@
 
+## Measurements 
 ## Measurements 
@@
 
-We run the model in R [@citeR] using the `rstanarm` package of @rstanarm, `here` package of @here and `model_summary` package of @model_summary, we use the default priors from `rstanarm`
+In `R` [@citeR], we run a logistic regression model in a Bayesian framework by using the `rstanarm` package of @rstanarm, `here` package of @here and `model_summary` package of @model_summary, we use the default priors from `rstanarm` in order to specific prior probability distributions for each of the parameters in the model.
+Logistic regression model is used to identify the correlation or relationship between some predictor variables and a outcome variable [@rohan], which is best fit with our research because we aim to identify the relationship between gender and race and support of Biden.
 
@@
 
+## Model justification
+
+We expect a positive relationship between the size of the wings and time spent aloft. Logistic regression models learn and predict very quickly
+Fast, because logistic regression is a linear model, its decision function is a very simple linear function, so its computational complexity is low.
+Logistic regression model is easy to interpret, and the coefficient of the model can give the degree of influence of each feature on the model.
+This can be used in real business applications to help decision makers better understand the model's predictions.
+In addition, logistic regression models can handle large scale data well, because logistic regression models only need to dimension a small number of parameters to adapt well to a large number of parameters.
+
+We can use maths by including latex between dollar signs, for instance $\theta$.
 ## Model justification
@@
 Yet, Black (−1.030) and Other  (−0.092) decrease support for Biden by looking at the coefficients.
-
 # Discussion {#sec-Discussion}

### 2024-03-17 scripts/04-model.R
Delete scripts/04-model.R

@@ -1,53 +1,0 @@
-#### Preamble ####
-# Purpose: Models... [...UPDATE THIS...]
-# Author: Yang Zhou & Yuean Wang & Dong Jun Yoon 
-# Date: 12 March 2024 
-# Contact: cocoyang.zhou@utoronto.ca & dongjun.yoon@mail.utoronto.ca & yuean.wang@mail.utoronto.ca
-# License: MIT
-# Pre-requisites: No
-# Any other information needed? No
-
-
-#### Workspace setup ####
-library(tidyverse)
-library(rstanarm)
-library(modelsummary)
-
-#### Read data ####
-analysis_data <- read_csv("data/analysis_data/analysis_data.csv")
-
-### Model data ####
-set.seed(853)
-
-ces2022_reduced <- 
-  ces2022 |> 
-  slice_sample(n = 500)
-
-us_political_preferences <-
-  stan_glm(
-    factor(voted_for) ~ gender4 + race,
-    data = analysis_data,
-    family = binomial(link = "logit"),
-    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_intercept = 
-      normal(location = 0, scale = 2.5, autoscale = TRUE),
-    seed = 853
-  )
-
-
-
-#### Save model ####
-saveRDS(
-  us_political_preferences,
-  file = "model/first_model.rds"
-)
-
-
-modelsummary(
-  list(
-    "Support Biden" = us_political_preferences
-  ),
-  statistic = "mad"
-)
-
-

### 2024-03-17 scripts/03-test_data.R
Delete scripts/03-test_data.R

@@ -1,21 +1,0 @@
-#### Preamble ####
-# Purpose: Tests... [...UPDATE THIS...]
-# Author: Yang Zhou & Yuean Wang & Dong Jun Yoon 
-# Date: 12 March 2024 
-# Contact: cocoyang.zhou@utoronto.ca & dongjun.yoon@mail.utoronto.ca & yuean.wang@mail.utoronto.ca
-# License: MIT
-# Pre-requisites: No
-# Any other information needed? No
-
-
-#### Workspace setup ####
-library(tidyverse)
-library(testthat)
-
-#### Test data ####
-simulate_data <- read.csv("data/simulate_data/simulate_data.csv")
-test_that("Check class", {
-  expect_type(cleaned_data$race, "character")
-  expect_type(cleaned_data$gender, "character")
-})
-

### 2024-03-17 scripts/02-data_cleaning.R
Delete scripts/02-data_cleaning.R

@@ -1,53 +1,0 @@
-#### Preamble ####
-# Purpose: Cleans the raw plane data recorded by two observers..... [...UPDATE THIS...]
-# Author: Yang Zhou & Yuean Wang & Dong Jun Yoon 
-# Date: 12 March 2024 
-# Contact: cocoyang.zhou@utoronto.ca & dongjun.yoon@mail.utoronto.ca & yuean.wang@mail.utoronto.ca
-# License: MIT
-# Pre-requisites: No
-# Any other information needed? No
-
-#### Workspace setup ####
-library(tidyverse)
-
-#### Clean data ####
-raw_data <- read_csv("data/raw_datas/raw_datas.csv")
-
-cleaned_data <-
-  raw_data |>
-  filter(votereg == 1,
-         presvote20post %in% c(1, 2),
-         gender4 %in% c(1, 2)) |> 
-  mutate(
-    voted_for = if_else(presvote20post == 1, "Biden", "Trump"),
-    voted_for = as_factor(voted_for),
-    gender = if_else(gender4 == 1, "Male", "Female"),
-    race = case_when(
-      race == 1 ~ "White",
-      race == 2 ~ "Black",
-      race == 3 ~ "Hispanic",
-      race == 4 ~ "Asian",
-      race == 5 ~ "Native American",
-      race == 6 ~ "Middle Eastern",
-      race == 7 ~ "Two or more races",
-      race == 8 ~ "Other"
-    ),
-    race = factor(
-      race,
-      levels = c(
-        "White",
-        "Black",
-        "Hispanic",
-        "Asian",
-        "Native American",
-        "Middle Eastern",
-        "Two or more races",
-        "Other"
-      )
-    )
-  ) |>
-  select(voted_for, gender4, race)
-
-
-#### Save data ####
-write_csv(cleaned_data, "data/analysis_data/analysis_data.csv")

### 2024-03-17 scripts/01-download_data.R
Delete scripts/01-download_data.R

@@ -1,30 +1,0 @@
-#### Preamble ####
-# Purpose: Downloads and saves the data from [...UPDATE THIS...]
-# Author: Yang Zhou & Yuean Wang & Dong Jun Yoon 
-# Date: 12 March 2024 
-# Contact: cocoyang.zhou@utoronto.ca & dongjun.yoon@mail.utoronto.ca & yuean.wang@mail.utoronto.ca
-# License: MIT
-# Pre-requisites: No
-# Any other information needed? No
-
-
-#### Workspace setup ####
-library(dataverse)
-library(tidyverse)
-
-
-#### Download data ####
-ces2022 <-
-  get_dataframe_by_name(
-    filename = "CCES22_Common_OUTPUT_vv_topost.csv",
-    dataset = "10.7910/DVN/PR4L8P",
-    server = "dataverse.harvard.edu",
-    .f = read_csv
-  ) |>
-  select(votereg, presvote20post, race, gender4)
-
-write_csv(ces2022, "data/raw_datas/raw_datas.csv")
-
-
-
-         

### 2024-03-17 scripts/04-model.R
Add files via upload

@@ -1,0 +1,52 @@
+#### Preamble ####
+# Purpose: Models the relationship between voting preference and predictors of gender and race by logistic regression. It will implement with Bayesian methods via the rstanarm package.
+# Author: Yang Zhou, Yuean Wang, Dong Jun Yoon
+# Date: 14 March 2024
+# Contact: cocoyang.zhou@mail.utoronto.ca, yuean.wang@mail.utoronto.ca, dongjun.yoon@mail.utoronto.ca
+# License: MIT
+
+
+
+#### Workspace setup ####
+library(tidyverse)
+library(rstanarm)
+library(modelsummary)
+
+#### Read data ####
+analysis_data <- read_csv("data/analysis_data/analysis_data.csv")
+
+### Model data ####
+set.seed(853)
+
+ces2022_reduced <- 
+  ces2022 |> 
+  slice_sample(n = 500)
+
+us_political_preferences <-
+  stan_glm(
+    factor(voted_for) ~ gender4 + race,
+    data = analysis_data,
+    family = binomial(link = "logit"),
+    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
+    prior_intercept = 
+      normal(location = 0, scale = 2.5, autoscale = TRUE),
+    seed = 853
+  )
+
+
+
+#### Save model ####
+saveRDS(
+  us_political_preferences,
+  file = "model/first_model.rds"
+)
+
+
+modelsummary(
+  list(
+    "Support Biden" = us_political_preferences
+  ),
+  statistic = "mad"
+)
+
+

### 2024-03-17 scripts/00-simulate_data.R
Delete scripts/00-simulate_data.R

@@ -1,41 +1,0 @@
-#### Preamble ####
-# Purpose: Simulates... 
-# Author: Yang Zhou & Yuean Wang & Dong Jun Yoon 
-# Date: 12 March 2024
-# Contact: cocoyang.zhou@utoronto.ca & dongjun.yoon@mail.utoronto.ca & yuean.wang@mail.utoronto.ca 
-# License: MIT
-# Pre-requisites: No
-# Any other information needed? No
-
-
-#### Workspace setup ####
-library(tidyverse)
-library(dplyr)
-
-#### Simulate data ####
-set.seed(853)
-
-num_obs <- 800
-
-us_political_preferences <- tibble(
-  race = sample(0:4, size = num_obs, replace = TRUE),
-  gender = sample(1:2, size = num_obs, replace = TRUE),
-  support_prob = ((race + gender) / 5),
-) |>
-  mutate(
-    supports_biden = if_else(runif(n = num_obs) < support_prob, "yes", "no"),
-    race = case_when(
-      race == 0 ~ "White",
-      race == 1 ~ "Black",
-      race == 2 ~ "Hispanic",
-      race == 3 ~ "Asian",
-      race == 4 ~ "Other"
-    ),
-    gender = if_else(gender == 1, "Male", "Female")
-  ) |>
-  select(-support_prob, supports_biden, race, gender)
-
-
-
-
-write.csv(us_political_preferences, "data/simulate_data/simulate_data.csv")

### 2024-03-17 scripts/00-simulate_data.R
Add files via upload

@@ -1,0 +1,40 @@
+#### Preamble ####
+# Purpose: Simulates political support in United States data based on gender and race
+# Author: Yang Zhou, Yuean Wang, Dong Jun Yoon
+# Date: 14 March 2024 
+# Contact: cocoyang.zhou@mail.utoronto.ca, yuean.wang@mail.utoronto.ca, dongjun.yoon@mail.utoronto.ca
+# License: MIT
+
+
+
+#### Workspace setup ####
+library(tidyverse)
+library(dplyr)
+
+#### Simulate data ####
+set.seed(853)
+
+num_obs <- 800
+
+us_political_preferences <- tibble(
+  race = sample(0:4, size = num_obs, replace = TRUE),
+  gender = sample(1:2, size = num_obs, replace = TRUE),
+  support_prob = ((race + gender) / 5),
+) |>
+  mutate(
+    supports_biden = if_else(runif(n = num_obs) < support_prob, "yes", "no"),
+    race = case_when(
+      race == 0 ~ "White",
+      race == 1 ~ "Black",
+      race == 2 ~ "Hispanic",
+      race == 3 ~ "Asian",
+      race == 4 ~ "Other"
+    ),
+    gender = if_else(gender == 1, "Male", "Female")
+  ) |>
+  select(-support_prob, supports_biden, race, gender)
+
+
+
+
+write.csv(us_political_preferences, "data/simulate_data/simulate_data.csv")

### 2024-03-17 paper/paper.qmd
Update paper.qmd

@@
 ## Measurements 
-## Measurements 
 The collected dataset from the Cooperative Election Study (CES) offers a comprehensive view of U.S.
@@
 We can use maths by including latex between dollar signs, for instance $\theta$.
-## Model justification
-
-We expect a positive relationship between the size of the wings and time spent aloft. Logistic regression models learn and predict very quickly
-Fast, because logistic regression is a linear model, its decision function is a very simple linear function, so its computational complexity is low.
-Logistic regression model is easy to interpret, and the coefficient of the model can give the degree of influence of each feature on the model.
-This can be used in real business applications to help decision makers better understand the model's predictions.
-In addition, logistic regression models can handle large scale data well, because logistic regression models only need to dimension a small number of parameters to adapt well to a large number of parameters.
-
-We can use maths by including latex between dollar signs, for instance $\theta$.
 
@@
 
-From the @tbl-model-summary-tableLogistic, with the constant variable, raceAsian, the intercept is -0.462 which means that the support for Biden decreases by about 0.784 units while all other variables remain the same.
+From the @tbl-model-summary-tableLogistic , with the constant variable, raceAsian, the intercept is -0.462 which means that the support for Biden decreases by about 0.784 units while all other variables remain the same.
 The following race, Hispanic (0.354), Middle Eastern (0.535), White (0.940), Native American (1.245), Two or more races (1.372) has stronger/ increasing their support for stronger/ increasing their support for Biden; in this case, the mixed race people have the strongest support for Biden.

### 2024-03-17 paper/paper.qmd
Update paper.qmd

@@
 1.Males are less likely to support Biden than Females,women most likely to vote for Biden,
-2.Middle Eastern, Hispanic, Black and Asian individuals are more likely to vote and show support for Biden.
+2.Hispanic, Middle Eastern, White, Native American, and Two or more races are more likely to support Biden. Black people tend to show less support for Biden.
 
@@
 
-## Middle Eastern, Hispanic, Black and Asian individuals are more likely to vote and show support for Biden.
+## Hispanic, Middle Eastern, White, Native American, and Two or more races are more likely to support Biden. Black people tend to show less support for Biden.
 
-Based on the analysis of @fig-vote, located under 2.6 Measurement, we can find out that Middle Eastern, Hispanic, Black and Asian individuals are more likely to vote and show support for Biden.
+Based on the analysis of @fig-vote, located under 2.6 Measurement, we can find out that Middle Eastern, Hispanic, and Asian individuals are more likely to vote and show support for Biden.
 In the graph we provided, we can easily tell that votes for Biden are higher than votes for Trump for certain races.
-For example, Black individuals have a total vote of 5293 individuals for Biden, however only 642 individuals support and vote for Trump.
-This same trend can also be observed in races such as Middle Eastern, Hispanic, Black and Asian individuals.
+For example, Hispanic individuals have a total vote of 2481 individuals for Biden, however only 1210 individuals support and vote for Trump.
+This same trend can also be observed in races such as Middle Eastern, Hispanic, and Asian individuals.
 Additionally, in recent elections, among Asian American/Pacific Islander, Black, Hispanic, and white voters, the number of women voters has exceeded the number of male voters.
 The gender gap in voter turnout rates is the largest for Black voters.
+In @tbl-model-summary-tableLogistic of our paper, we observe a negative coefficient for black people (−1.030) in support for Biden, indicating that Black people are displaying less support and fewer votes for Biden.
+The coefficient represents the logarithm of the anticipated variance in backing for Biden in contrast to Trump.
+When the coefficient values are negative, which means the voters decrease their support in Biden.
+Whereas, when the values are greater and equal to zero (positive) meaning the voters increase their support for Biden.
 Women have also voted at higher rates than men among Hispanic and white voters in all presidential elections since the 1980s.

### 2024-03-17 paper/paper.qmd
Update paper.qmd

@@
 ---
-title: "Political Support in the United States'"
+title: "Demographic Groups with Stronger Biden Support in the Election Races'"
 author: 

### 2024-03-17 paper/paper.qmd
Update paper.qmd

@@
 
-Throughout the paper, the data utilized for analysis, including both survey and census data, measurements, is in {#sec-data}.
-Following that, {#sec-model} introduces the model designed to generalize patterns and forecast election outcomes.
+Throughout the paper, the data utilized for analysis, including both survey and census data, measurements, is in Section 2.
+Following that, our estimand is the probability that an individual voted for Biden or Trump based on three characteristics; their gender, race, and ownership of a gun.
+The reason for this choice will be further examined in Section 3.
+Section 3 introduces the model designed to generalize patterns and forecast election outcomes.
 It will talk about how the model is set up and model justification.
-In {#sec-results}, I will talk about the predicted results derived from the model, this includes the result of the model.
-Lastly, {#sec-Discussion} contains more detailed results in a broader context and addresses weaknesses of this paper as well as the future explorations.
-This paper uses the programming language `R`[@citeR] .
-The analysis, the model and the visualizations use the following packages: `dplyr`[@dplyr],  `tidyverse`[@tidyverse], `ggplot2`[@ggplot], `knitr` [@knitr],  `here` [@here] , and `kableExtra` [@kableExtra],`modelsummary`[@model_summary], and `rstanarm`[@rstanarm].
+In Section 4, I will talk about the predicted results derived from the model, this includes the result of the model.
+Lastly, Section 5 contains more detailed results in a broader context and addresses weaknesses of this paper as well as the future explorations.
+This paper uses the programming language R (R Core Team 2022).
+The analysis, the model and the visualizations use the following packages: ipumsr (Greg Freedman Ellis, Derek Burk, and Finn Roberts 2024), dplyr (Wickham et al.
+2023), readr (Wickham, Hester, and Bryan 2024), tidyr (Wickham, Vaughan, and Girlich 2024), arrow (Richardson et al.
+2024), ggplot2 (Wickham 2016), knitr (Xie 2014), statebins (Rudis 2020), modelsi (Arel-Bundock 2022), broom (Robinson, Hayes, and Couch 2023), here (Müller 2020), and kableExt
+2024).
 

### 2024-03-17 paper/paper.qmd
Update paper.qmd

@@
   - Yang Zhou
-thanks: "Code and data are available at: <https://github.com/yangzhoucoco/Political-support-in-the-United-States.git.>"
+thanks: "Code and data are available at: <https://github.com/yangzhoucoco/Demographic-Groups-with-Stronger-Biden-Support-in-the-Election-Races >"
 date: today

### 2024-03-17 paper/paper.qmd
Final

@@
 
-ces2022_table <- ces2022 |>
-  kable("html", booktabs = TRUE, caption = "Brief summary of variables types") |>
+ces2022 |> slice_head(n = 10) |>
+  kable(booktabs = TRUE, caption = "Brief summary of variables types") |>
   kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)
-
-print(ces2022_table)
 ```
@@
 ```
-   After downloading `dataverse` [@dataverse], We using `get_dataframe_by_name` [@get_dataframe_by_name] to access the CES.
+   After downloading `dataverse` [@dataverse], We using `get_dataframe_by_name` to access the CES.
 We select and save the data that we are most care about, which are `votereg`, `presvote20post`, `race`, and `gender4`.

### 2024-03-17 scripts/04-model.R
Delete scripts/04-model.R

@@ -1,52 +1,0 @@
-#### Preamble ####
-# Purpose: Models the relationship between voting preference and predictors of gender and race by logistic regression. It will implement with Bayesian methods via the rstanarm package.
-# Author: Yang Zhou, Yuean Wang, Dong Jun Yoon
-# Date: 14 March 2024
-# Contact: cocoyang.zhou@mail.utoronto.ca, yuean.wang@mail.utoronto.ca, dongjun.yoon@mail.utoronto.ca
-# License: MIT
-
-
-
-#### Workspace setup ####
-library(tidyverse)
-library(rstanarm)
-library(modelsummary)
-
-#### Read data ####
-analysis_data <- read_csv("data/analysis_data/analysis_data.csv")
-
-### Model data ####
-set.seed(853)
-
-ces2022_reduced <- 
-  ces2022 |> 
-  slice_sample(n = 500)
-
-us_political_preferences <-
-  stan_glm(
-    factor(voted_for) ~ gender4 + race,
-    data = analysis_data,
-    family = binomial(link = "logit"),
-    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_intercept = 
-      normal(location = 0, scale = 2.5, autoscale = TRUE),
-    seed = 853
-  )
-
-
-
-#### Save model ####
-saveRDS(
-  us_political_preferences,
-  file = "model/first_model.rds"
-)
-
-
-modelsummary(
-  list(
-    "Support Biden" = us_political_preferences
-  ),
-  statistic = "mad"
-)
-
-

### 2024-03-17 paper/paper.qmd
Final

@@
 
-Throughout the paper, the data utilized for analysis, including both survey and census data, measurements, is in Section 2.
-Following that, our estimand is the probability that an individual voted for Biden or Trump based on three characteristics; their gender, race, and ownership of a gun.
-The reason for this choice will be further examined in Section 3.
-Section 3 introduces the model designed to generalize patterns and forecast election outcomes.
+Throughout the paper, the data utilized for analysis, including both survey and census data, measurements, is in {#sec-data}.
+Following that, {#sec-model} introduces the model designed to generalize patterns and forecast election outcomes.
 It will talk about how the model is set up and model justification.
-In Section 4, I will talk about the predicted results derived from the model, this includes the result of the model.
-Lastly, Section 5 contains more detailed results in a broader context and addresses weaknesses of this paper as well as the future explorations.
-This paper uses the programming language R (R Core Team 2022).
-The analysis, the model and the visualizations use the following packages: ipumsr (Greg Freedman Ellis, Derek Burk, and Finn Roberts 2024), dplyr (Wickham et al.
-2023), readr (Wickham, Hester, and Bryan 2024), tidyr (Wickham, Vaughan, and Girlich 2024), arrow (Richardson et al.
-2024), ggplot2 (Wickham 2016), knitr (Xie 2014), statebins (Rudis 2020), modelsi (Arel-Bundock 2022), broom (Robinson, Hayes, and Couch 2023), here (Müller 2020), and kableExt
-2024).
+In {#sec-results}, I will talk about the predicted results derived from the model, this includes the result of the model.
+Lastly, {#sec-Discussion} contains more detailed results in a broader context and addresses weaknesses of this paper as well as the future explorations.
+This paper uses the programming language `R`[@citeR] .
+The analysis, the model and the visualizations use the following packages: `dplyr`[@dplyr],  `tidyverse`[@tidyverse], `ggplot2`[@ggplot], `knitr` [@knitr],  `here` [@here] , and `kableExtra` [@kableExtra],`modelsummary`[@model_summary], and `rstanarm`[@rstanarm].
 

### 2024-03-17 paper/paper.qmd
Final

@@
 # Results {#sec-results}
-Our results are summarized in @tbl-model-summary-tableLogistic  regression is a common classification algorithm used to predict binary classification problems.
+Our results are summarized in @tbl-model-summary-tableLogistic, regression is a common classification algorithm used to predict binary classification problems.
 In logistic regression, the probability that a sample belongs to a certain class is determined by mapping the input data to a probability range between 0 and 1 using a logical function, such as the sigmoid function.
@@
 
-From the @tbl-model-summary-tableLogistic , with the constant variable, raceAsian, the intercept is -0.462 which means that the support for Biden decreases by about 0.784 units while all other variables remain the same.
+From the @tbl-model-summary-tableLogistic, with the constant variable, raceAsian, the intercept is -0.462 which means that the support for Biden decreases by about 0.784 units while all other variables remain the same.
 The following race, Hispanic (0.354), Middle Eastern (0.535), White (0.940), Native American (1.245), Two or more races (1.372) has stronger/ increasing their support for stronger/ increasing their support for Biden; in this case, the mixed race people have the strongest support for Biden.
